### 2023-01-28 paper/paper.tex
initial commit

% CVPR 2022 Paper Template
% based on the CVPR template provided by Ming-Ming Cheng (https://github.com/MCG-NKU/CVPR_Template)
% modified and extended by Stefan Roth (stefan.roth@NOSPAMtu-darmstadt.de)

\documentclass[10pt,twocolumn,letterpaper]{article}

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
\usepackage[review]{cvpr}      % To produce the REVIEW version
%\usepackage{cvpr}              % To produce the CAMERA-READY version
%\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, e.g. with the
% file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete
% ReviewTempalte.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you
%  should be clear).
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}

% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{*****} % *** Enter the CVPR Paper ID here
\def\confName{CVPR}
\def\confYear{2023}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Visual Geolocalization:
mapping images to GPS}

\author{Testa Mario\\
PoliTo\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Cambria Paolo\\
PoliTo\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
\and
Ciciriello Giuseppe\\
PoliTo\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
In this work, we develop a theoretical and experimental framework to study the effect of CosFace loss function to localize unseen images. Our theory extract the N-top retrieved images, with their geo-tag, the retrieval is performed as a k-Nearest Neighbour search. Finally, we conduct a thorough ablation study of the loss function by changing it with SphereFace and ArcFace loss functions. We then conducted experiments on image recognition benchmarks.
%   The ABSTRACT is to be in fully justified italicized text, at the top of the left-hand column, below the author and affiliation information.
%   Use the word ``Abstract'' as the title, in 12-point Times, boldface type, centered relative to the column, initially capitalized.
%   The abstract is to be in 10-point, single-spaced type.
%   Leave two blank lines after the Abstract, then begin the main text.
%   Look at previous CVPR abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}

Please follow the steps outlined below when submitting your manuscript to the IEEE Computer Society Press.
This style guide now has several important modifications (for example, you are no longer warned against the use of sticky tape to attach your artwork to the paper), so all authors should read this new version.

%-------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

Please refer to the author guidelines on the \confName\ \confYear\ web page for a
discussion of the policy on dual submissions.

\subsection{Paper length}
Papers, excluding the references section, must be no longer than eight pages in length.
The references section will not be included in the page count, and there is no limit on the length of the references section.
For example, a paper of eight pages with two pages of references would have a total length of 10 pages.
{\bf There will be no extra page charges for \confName\ \confYear.}

Overlength papers will simply not be reviewed.
This includes papers where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for supervised revisions of manuscripts.
The reviewing process cannot determine the suitability of the paper for presentation in eight pages if it is reviewed in eleven.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the version submitted for review.
The ruler is provided in order that reviewers may comment on particular lines in the paper without circumlocution.
If you are preparing a document using a non-\LaTeX\ document preparation system, please arrange for an equivalent ruler to appear on the final output pages.
The presence or absence of the ruler should not change the appearance of any other content on the page.
The camera-ready copy should not contain a ruler.
(\LaTeX\ users may use options of cvpr.sty to switch between different versions.)

Reviewers:
note that the ruler measurements do not align well with lines in the paper --- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
Just use fractional references (\eg, this line is $087.5$), although in most cases one would expect that the approximate location will be adequate.

\subsection{Paper ID}
Make sure that the Paper ID from the submission system is visible in the version submitted for review (replacing the ``*****'' you see in this document).
If you are using the \LaTeX\ template, \textbf{make sure to update paper ID in the appropriate place in the tex file}.

\subsection{Mathematics}

Please number all of your sections and displayed equations as in these examples:
\begin{equation}
  E = m\cdot c^2
  \label{eq:important}
\end{equation}
and
\begin{equation}
  v = a\cdot t.
  \label{eq:also-important}
\end{equation}
It is important for readers to be able to refer to any particular equation.
Just because you did not refer to it in the text does not mean some future reader might not need to refer to it.
It is cumbersome to have to use circumlocutions like ``the equation second from the top of page 3 column 1''.
(Note that the ruler will not be present in the final copy, so is not an alternative to equation numbers).
All authors will benefit from reading Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind review.
Blind review does not mean that one must remove citations to one's own work---in fact it is often impossible to review a paper unless the previous citations are known and available.

Blind review means that you do not use the words ``my'' or ``our'' when citing previous work.
That is all.
(But see below for tech reports.)

Saying ``this builds on the work of Lucy Smith [1]'' does not say that you are Lucy Smith;
it says that you are building on her work.
If you are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith and Jones show in [7]'' and at the end of the paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our previous paper [1], and show it to be inferior to all previously known methods.
   Why the previous paper was accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:
\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the  paper of Smith \etal [1], and show it to be inferior to all previously known methods.
   Why the previous paper was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a fundamental contribution to human knowledge''. Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time, which covers similar or overlapping material, you may need to refer to that submission in order to explain the differences, just as you would if you had previously published related work.
In such cases, include the anonymized parallel submission~\cite{Authors14} as supplemental material and cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324, Supplied as supplemental material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be found elsewhere, and refer them to a technical report.
For conference submissions, the paper must stand on its own, and not {\em require} the reviewer to go to a tech report for further details.
Thus, you may say in the body of the paper ``further details may be found in~\cite{Authors14b}''.
Then submit the tech report as supplemental material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool that is widely known to be restricted to a single institution.
For example, let's say it's 1969, you have solved a key problem on the Apollo lander, and you believe that the CVPR70 audience would like to hear about your
solution.
The work is a development of your celebrated 1968 paper entitled ``Zero-g frobnication: How being the only people in the world with access to the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.
Do not write ``We show how to improve our previous work [Anonymous, 1968].
This time we tested the algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors.
Instead write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.
   This system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] did not  handle case B properly.
   Ours handles it by including a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo lunar lander, and went all the way to the moon, don't you know.
   It displayed the following behaviours, which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention, reads better than the first version, and does not explicitly name you as the authors.
A reviewer might think it likely that the new paper was written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been contracted to solve problem B.
\medskip

\noindent
FAQ\medskip\\
{\bf Q:} Are acknowledgements OK?\\
{\bf A:} No.  Leave them for the final copy.\medskip\\
{\bf Q:} How do I cite my results reported in open challenges?
{\bf A:} To conform with the double-blind review policy, you can report results of other challenge participants together with your results in your paper.
For your results, however, you should not identify yourself and should not mention your participation in the challenge.
Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\

\begin{figure}[t]
  \centering
  \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}

   \caption{Example of caption.
   It is set in Roman so that mathematics (always set in Roman: $B \sin A = A \sin B$) may be included without an ugly clash.}
   \label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a sentence-ending space.
So \eg is correct, {\em e.g.} is not.
The provided \verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word).
If you use the \verb'\etal' macro provided, then you need not worry about double periods when used at the end of a sentence as in Alpher \etal.
However, use it only when there are three or more authors.
Thus, the following is correct:
   ``Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...'' because reference~\cite{Alpher03} has just two authors.

% Update the cvpr.cls to do the following automatically.
% For this citation style, keep multiple citations in numerical (not
% chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
% \cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
  \centering
  \begin{subfigure}{0.68\linewidth}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
    \caption{An example of a subfigure.}
    \label{fig:short-a}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.28\linewidth}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
    \caption{Another example of a subfigure.}
    \label{fig:short-b}
  \end{subfigure}
  \caption{Example of a short caption, which should be centered.}
  \label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}
\label{sec:formatting}

All text must be in a two-column format.
The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
The main title (on the first page) should begin 1 inch (2.54 cm) from the top edge of the page.
The second and following pages should begin 1 inch (2.54 cm) from the top edge.
On all pages, the bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area $6\frac{7}{8}$ inches (17.46 cm) wide by $8\frac{7}{8}$ inches (22.54 cm)
high.
%
Page numbers should be in the footer, centered and $\frac{3}{4}$ inches from the bottom of the page.
The review version should have page numbers, yet the final version submitted as camera ready should not show any page numbers.
The \LaTeX\ template takes care of this when used properly.

%-------------------------------------------------------------------------
\subsection{Type style and fonts}

Wherever Times is specified, Times Roman may also be used.
If neither is available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE.
Center the title $1\frac{3}{8}$ inches (3.49 cm) from the top edge of the first page.
The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and adverbs;
do not capitalize articles, coordinate conjunctions, or prepositions (unless the title begins with such a word).
Leave two blank lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type.
This information is to be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT.
Type main text in 10-point Times, single-spaced.
Do NOT use double-spacing.
All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
Make sure your text is fully justified---that is, flush left and flush right.
Please do not place any additional blank lines between paragraphs.

Figure and table captions should be 9-point Roman type as in \cref{fig:onecol,fig:short}.
Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-, second-, and third-order headings.

FIRST-ORDER HEADINGS.
(For example, {\large \bf 1. Introduction}) should be Times 12-point boldface, initially capitalized, flush left, with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS.
(For example, { \bf 1.1. Database elements}) should be Times 11-point boldface, initially capitalized, flush left, with one blank line before, and one after.
If you require a third-order heading (we discourage it), use 10-point Times, boldface, initially capitalized, flush left, preceded by one blank line, followed by a period and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote{This is what a footnote looks like.
It often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral observations in the text (within parentheses, if you prefer, as in this sentence).
If you wish to use a footnote, place it at the bottom of the column on the page on which it is referenced.
Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{Cross-references}

For the benefit of author(s) and readers, please use the
{\small\begin{verbatim}
  \cref{...}
\end{verbatim}}  command for cross-referencing to figures, tables, equations, or sections.
This will automatically insert the appropriate label alongside the cross-reference as in this example:
\begin{quotation}
  To see how our method outperforms previous work, please see \cref{fig:onecol} and \cref{tab:example}.
  It is also possible to refer to multiple targets as once, \eg~to \cref{fig:onecol,fig:short-a}.
  You may also return to \cref{sec:formatting} or look at \cref{eq:also-important}.
\end{quotation}
If you do not wish to abbreviate the label, for example at the beginning of the sentence, you can use the
{\small\begin{verbatim}
  \Cref{...}
\end{verbatim}}
command. Here is an example:
\begin{quotation}
  \Cref{fig:onecol} is also quite important.
\end{quotation}

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times, single-spaced, at the end of your paper.
When referenced in the text, enclose the citation number in square brackets, for
example~\cite{Authors14}.
Where appropriate, include page numbers and the name(s) of editors of referenced books.
When you cite multiple papers at once, please make sure that you cite them in numerical order like this \cite{Alpher02,Alpher03,Alpher05,Authors14b,Authors14}.
If you use the template as advised, this will be taken care of automatically.

\begin{table}
  \centering
  \begin{tabular}{@{}lc@{}}
    \toprule
    Method & Frobnability \\
    \midrule
    Theirs & Frumpy \\
    Yours & Frobbly \\
    Ours & Makes one's heart Frob\\
    \bottomrule
  \end{tabular}
  \caption{Results.   Ours is better.}
  \label{tab:example}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.
In \LaTeX, avoid using the \texttt{center} environment for this purpose, as this adds potentially unwanted whitespace.
Instead use
{\small\begin{verbatim}
  \centering
\end{verbatim}}
at the beginning of your figure.
Please ensure that any point you wish to make is resolvable in a printed copy of the paper.
Resize fonts in figures to match the font in the body text, and choose line widths that render effectively in print.
Readers (and reviewers), even of an electronic copy, may choose to print your paper in order to read it.
You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.pdf}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the \confName\ \confYear\ web page for a discussion of the use of color in your document.

If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit your finished paper.
We MUST have this form before your paper can be published in the proceedings.

Please direct any questions to the production editor in charge of these proceedings at the IEEE Computer Society Press:
\url{https://www.computer.org/about/contact}.

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}

### 2023-01-29 train_only.py
paper base

@@ -1,186 +1,187 @@
 
-import sys
-import torch
-import logging
-import numpy as np
-from tqdm import tqdm
-import multiprocessing
-from datetime import datetime
-import torchvision.transforms as T
-import custom_augmentations as CA
-import test
-import util
-import parser
-import commons
-import cosface_loss
-import new_cosface_loss
-import sphereface_loss
-import arcface_loss
-import augmentations
-from model import network
-from datasets.test_dataset import TestDataset
-from datasets.train_dataset import TrainDataset
+if __name__ ==  '__main__':
+    import sys
+    import torch
+    import logging
+    import numpy as np
+    from tqdm import tqdm
+    import multiprocessing
+    from datetime import datetime
+    import torchvision.transforms as T
+    import custom_augmentations as CA
+    import test
+    import util
+    import myparser
+    import commons
+    import cosface_loss
+    import new_cosface_loss
+    import sphereface_loss
+    import arcface_loss
+    import augmentations
+    from model import network
+    from datasets.test_dataset import TestDataset
+    from datasets.train_dataset import TrainDataset
 
-torch.backends.cudnn.benchmark = True  # Provides a speedup
+    torch.backends.cudnn.benchmark = True  # Provides a speedup
 
-args = parser.parse_arguments()
-start_time = datetime.now()
-output_folder = f"AML23-CosPlace/model/results/best_{start_time.strftime('%Y-%m-%d_%H-%M-%S')}"
-commons.make_deterministic(args.seed)
-commons.setup_logging(output_folder, console="debug")
-logging.info(" ".join(sys.argv))
-logging.info(f"Arguments: {args}")
-logging.info(f"The outputs are being saved in {output_folder}")
+    args = myparser.parse_arguments()
+    start_time = datetime.now()
+    output_folder = f"AML23-CosPlace/model/results/best_{start_time.strftime('%Y-%m-%d_%H-%M-%S')}"
+    commons.make_deterministic(args.seed)
+    commons.setup_logging(output_folder, console="debug")
+    logging.info(" ".join(sys.argv))
+    logging.info(f"Arguments: {args}")
+    logging.info(f"The outputs are being saved in {output_folder}")
 
-#### Model
-model = network.GeoLocalizationNet(args.backbone, args.fc_output_dim)
+    #### Model
+    model = network.GeoLocalizationNet(args.backbone, args.fc_output_dim)
 
-logging.info(f"There are {torch.cuda.device_count()} GPUs and {multiprocessing.cpu_count()} CPUs.")
[…]

### 2023-01-29 paper/paper.tex
updated setup
paper update

@@
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{Visual Geolocalization:
-mapping images to GPS}
+\title{Visual Geolocaslization:
+mapping images o GPS}
 
-\author{Testa Mario\\
-PoliTo\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
+\author{Cambria Paolo - s301164\\
+Politecnico di Torino\\
+{\tt\small paolocambria@studenti.polito.it}
 \and
-Cambria Paolo\\
-PoliTo\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
+Ciciriello Giuseppe - 301953\\
+Politecnico di Torino\\
+{\tt\small giuseppe.ciciriello@studenti.polito.it}
 \and
-Ciciriello Giuseppe\\
-PoliTo\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
+Testa Mario - 292630\\
+Politecnico di Torino\\
+{\tt\small mario.testa@studenti.polito.it}
 }
@@
 %%%%%%%%% BODY TEXT
-\section{Introduction}
-\label{sec:intro}
+\section{Introduction}\label{sec:intro}
+Visual geo-localization (VG) [TODO CITE] is one of the most promising approaches in the field of computer vision [TODO CITE] and image localization,
+due to his importance in applications such as autonomous driving [TODO CITE C. McManus, W. Churchill, W. Maddern, A. Stewart, and
+P. Newman. Shady dealings: Robust, long-term visual localisation using illumination invariance. In Proc. Intl. Conf. on
+Robotics and Automation, 2014] or even augmented reality [TODO CITE 47 S. Middelberg, T. Sattler, O. Untzelmann, and L. Kobbelt.
+Scalable 6-DOF localization on mobile devices. In Proc.
+ECCV, 2014].
+VG usually consists of a place recognition task: given a query image of a place, its geographical location has to be roughly recognized and retrieved
+by finding the closest database geo-tagged images usually with a tolerance of few meters. 
+This task is extremely challenging due to the intrinsic dynamism of public places and different problems must be taken in account:
+there are a lot of moving objects which determine occlusion, enviromental changes, different illuminations during daylight and night time, season changing.
+Furthermore, most of the recent learning based VG methods focus on recognizing the location of images in a relatively small sized geographical area (e.g. a neighborhood), 
+which is not enough for concrete applications such as autonomous driving [TODO CITE] that operate in much larger areas such as whole cities. 
+\newline
+\textbf{Dataset}
+To achieve a VG task on a wider geographical area, a large representative dataset is required and as underlined by [TODO CITE GBERTON] the majority of 
+current datasets are either too small in the geographical coverage, or too sparse [TODO CITE]. Moreover, those datasets split the collected images into 
+disjoint sets for training and inference and this not suits a realistic use case, since the search query might be often an already seen place.
+For this reason it is recommendable to use the whole dataset to train the model, given also the cost of collecting the images for a consistent dataset.
+[TODO dire di SF-XL e Xs?]
+\newline
+\textbf{Training scalability}
+A such large dataset it's not so easy to exploit for training effectively a model. Many of the recent SOTA (state-of-the-art) methods take advantage
+of contrastive learning methods [TODO CITE], which can often depend on contrasting positive to negative examples across the training dataset [TODO CITE],
+a costly operation in terms of computation. 
+[TODO VALUTARE SE CITARE https://arxiv.org/pdf/1702.01238.pdf]
+[TODO citare gberton e dire che funziona su grandi paper]
+CosPlace [TODO citare] is an highly scalable training method, properly designed to work on larger dataset in the field of Geo-localization, in order to 
+overcome the costly computational needs required in this field and to successfully exploit such enormous amount of data to reach 
+SOTA results with compact descriptors.
 
+%---------------
 Please follow the steps outlined below when submitting your manuscript to the IEEE Computer Society Press.

### 2023-01-29 paper/paper.tex
added few sections and structure

@@
 %%%%%%%%% BODY TEXT
-\section{Introduction}\label{sec:intro}
+\section{Introduction}\label{sec:introduction}
 Visual geo-localization (VG) [TODO CITE] is one of the most promising approaches in the field of computer vision [TODO CITE] and image localization,
@@
 For this reason it is recommendable to use the whole dataset to train the model, given also the cost of collecting the images for a consistent dataset.
-[TODO dire di SF-XL e Xs?]
+[TODO dire di SF-XL e Xs? e toky onight??]
 \newline
@@
 SOTA results with compact descriptors.
+\newline
+\textbf{Contributions}
+In this paper we want to investigate how the work of [TODO citare Berton] can be improved for place recognition tasks.
+In particular we focus to generally improve the recall [todo explain?] on the SF-XS dataset [TODO citare dataset / aggiungerlo] and more specifically
+on a dataset in completely different brightness conditions such as Tokyo-Night [TODO CITARE DATASET / AGGIUNGERLO].
+Furthermore, we want to assess how CosPlace [TODO CITARE] behaves when the data quality is scarce, e.g. for occlusion and blurry photos.
 
-%---------------
-Please follow the steps outlined below when submitting your manuscript to the IEEE Computer Society Press.
-This style guide now has several important modifications (for example, you are no longer warned against the use of sticky tape to attach your artwork to the paper), so all authors should read this new version.
+Our contribution consists of:
+[TODO listare le contributions dopo che abbiamo i risultati ]
+[TODO conclusioni rapide]
 
 %-------------------------------------------------------------------------
-\subsection{Language}
+\section{Related Works}\label{sec:relatedworks}
+Visual geolocalization on large scale is commonly considered as an image retrieval task, in which the correctness is determined by an established
+tolerance (usually 25 meters) from the query's ground truth position [TODO CITE].    
+One of the most representative study in this field is NetVLAD [TODO CITE], which introduces the VLAD pooling layer  [TODO RIVEDERE FRASE copiata da GBerton]
+that pools extracted descriptors into a fixed image representation whose parameters are learnable via back-propagation.
+The retrieval task is performed by using the learned embeddings produced by a feature extraction backbone equipped with a head that implements VLAD pooling.
+[/TODO]
+[TODO aggiungere tutta la prte delle loss altrui con contrastive learning]
+[TODO parlare bene di cosplace]
+%-------------------------------------------------------------------------
+\section{Experiments}\label{sec:experiments}
+\subsection{Implementation Details}
+[TODO aggiungere roba su architettura cosplace]
+\subsection{Ablation}
+\textbf{Augmentation Pipeline}
+[TODO DA RIFINIRE]
+To improve the  ... we conducted a study on the augmentation pipeline by implementing 4 new augmentations on the images with a probability of 0.25 and a custom seed for
+reproducibily purposes.
+Due to the computational requirements, we were only able to perform this ablation on SF-XXS dataset, the results are reported below in table [TODO ADD TABLE REF]:
+[TODO AGGIUNGERE TABLE]
 
-All manuscripts must be in English.
+[TODO guardare extension b]
 
-\subsection{Dual submission}
-
-Please refer to the author guidelines on the \confName\ \confYear\ web page for a
-discussion of the policy on dual submissions.
-
-\subsection{Paper length}
-Papers, excluding the references section, must be no longer than eight pages in length.
-The references section will not be included in the page count, and there is no limit on the length of the references section.
-For example, a paper of eight pages with two pages of references would have a total length of 10 pages.
-{\bf There will be no extra page charges for \confName\ \confYear.}
-
-Overlength papers will simply not be reviewed.
-This includes papers where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
-Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.
-The reason such papers will not be reviewed is that there is no provision for supervised revisions of manuscripts.
-The reviewing process cannot determine the suitability of the paper for presentation in eight pages if it is reviewed in eleven.
-
-%-------------------------------------------------------------------------
 \subsection{The ruler}

### 2023-01-30 model_soup.py
fix: fixed model_soup directory

@@ -60,7 +60,7 @@ if __name__ == "__main__":
 
     args = parser.parse_arguments(is_training=False)
 
-    base_path = "model/{}/{}_best_model.pth"
+    base_path = "AML23-CosPlace/model/{}/{}_best_model.pth"
     models_directories=["cosface","sphereface","arcface"]
     val_rec = [52.4,61.0,53.3,50.5,47.6]
     models_list = []

### 2023-01-30 model_soup.py
fix: rename base_path

@@ -60,7 +60,7 @@ if __name__ == "__main__":
 
     args = parser.parse_arguments(is_training=False)
 
-    base_path = "AML23-CosPlace/model/{}/{}_best_model.pth"
+    base_path = "model/{}/{}_best_model.pth"
     models_directories=["cosface","sphereface","arcface"]
     val_rec = [52.4,61.0,53.3,50.5,47.6]
     models_list = []

### 2023-01-30 model_soup.py
fix: rename model_soup test_dataset

@@ -67,4 +67,4 @@ if __name__ == "__main__":
     for idx, model_path in enumerate(models_directories):
         m = load_model(base_path.format(model_path, model_path),args)
         models_list.append((m, val_rec[idx]))
-    greedy_soup(models_list, "tokyo_xs/test/", args)
+    greedy_soup(models_list, "small/test/", args)

### 2023-01-30 model_soup.py
fix: rename model_soup test_dataset

@@ -67,4 +67,4 @@ if __name__ == "__main__":
     for idx, model_path in enumerate(models_directories):
         m = load_model(base_path.format(model_path, model_path),args)
         models_list.append((m, val_rec[idx]))
-    greedy_soup(models_list, "tokyo_xs/test/", args)
+    greedy_soup(models_list, "/content/small/test/", args)

### 2023-01-30 model_soup.py
fix: renamed output folder

@@ -49,7 +49,7 @@ def greedy_soup(models_list, val_folder, args):
             greedy_soup_params = potential_greedy_soup_params
             print(f'Adding to soup.')
     experiment_name= "sample_soup"
-    torch.save(greedy_soup_params, f"soups/{experiment_name}/soup.pth") 
+    torch.save(greedy_soup_params, f"/content/AML23-CosPlace/soups/{experiment_name}/soup.pth") 
 
 
 def compare(m1):

### 2023-01-30 model_soup.py
fix: renamed output folder

@@ -49,7 +49,7 @@ def greedy_soup(models_list, val_folder, args):
             greedy_soup_params = potential_greedy_soup_params
             print(f'Adding to soup.')
     experiment_name= "sample_soup"
-    torch.save(greedy_soup_params, f"soups/{experiment_name}/soup.pth") 
+    torch.save(greedy_soup_params, f"soup.pth") 
 
 
 def compare(m1):

### 2023-01-30 model_soup.py
fix: rename output

@@ -49,7 +49,7 @@ def greedy_soup(models_list, val_folder, args):
             greedy_soup_params = potential_greedy_soup_params
             print(f'Adding to soup.')
     experiment_name= "sample_soup"
-    torch.save(greedy_soup_params, f"/content/AML23-CosPlace/soups/{experiment_name}/soup.pth") 
+    torch.save(greedy_soup_params, f"soup.pth") 
 
 
 def compare(m1):

### 2023-01-30 model_soup.py
fix: modify models involved in soup

@@ -49,7 +49,7 @@ def greedy_soup(models_list, val_folder, args):
             greedy_soup_params = potential_greedy_soup_params
             print(f'Adding to soup.')
     experiment_name= "sample_soup"
-    torch.save(greedy_soup_params, f"soup.pth") 
+    torch.save(greedy_soup_params, f"soup.pth")
 
 
 def compare(m1):
@@ -60,11 +60,11 @@ if __name__ == "__main__":
 
     args = parser.parse_arguments(is_training=False)
 
-    base_path = "model/{}/{}_best_model.pth"
-    models_directories=["cosface","sphereface","arcface"]
+    base_path = "model/{}"
+    models_directories=["cosface/cosface_best_model.pth","ablation_augmentation/erasing_full.pth","ablation_augmentation/gblur_occlusion_full.pth"]
     val_rec = [52.4,61.0,53.3,50.5,47.6]
     models_list = []
     for idx, model_path in enumerate(models_directories):
-        m = load_model(base_path.format(model_path, model_path),args)
+        m = load_model(base_path.format(model_path),args)
         models_list.append((m, val_rec[idx]))
     greedy_soup(models_list, "/content/small/test/", args)

### 2023-01-31 model_soup.py
fix: another try for greedy_soup

@@ -5,10 +5,11 @@ import torch
 from datetime import datetime
 import parser
 
-def load_model(path, args):
+def load_model(model_path,args):
     model = network.GeoLocalizationNet(args.backbone, args.fc_output_dim)
-    model_state_dict = torch.load(path)
+    model_state_dict = torch.load(model_path)
     
+    model.load_state_dict(delete_discriminator_layer(model_state_dict))
     return model
 
 def greedy_soup(models_list, val_folder, args):
@@ -21,7 +22,9 @@ def greedy_soup(models_list, val_folder, args):
         model = model.eval()
        
         sorted_models.append((model, val))
-        continue
+        recalls, recalls_str = test.test(args, val_ds, model)
+        print(recalls)
+        #continue
 
     sorted_models.sort(key=compare, reverse=True)
     greedy_soup_ingredients = [sorted_models[0][0]]
@@ -49,20 +52,29 @@ def greedy_soup(models_list, val_folder, args):
             greedy_soup_params = potential_greedy_soup_params
             print(f'Adding to soup.')
     experiment_name= "sample_soup"
-    torch.save(greedy_soup_params, f"soup.pth")
+    torch.save(greedy_soup_params, f"{experiment_name}.pth")
 
 
 def compare(m1):
     return m1[1]
 
+def delete_discriminator_layer(model):
+    if "discriminator.1.weight" in model:
+            del model["discriminator.1.weight"]
+            del model["discriminator.1.bias"]
+            del model["discriminator.3.weight"]
+            del model["discriminator.3.bias"]
+            del model["discriminator.5.weight"]
+            del model["discriminator.5.bias"]
+    return model
 
 if __name__ == "__main__":
 
     args = parser.parse_arguments(is_training=False)
 
     base_path = "model/{}"
-    models_directories=["cosface/cosface_best_model.pth","ablation_augmentation/erasing_full.pth","ablation_augmentation/gblur_occlusion_full.pth"]
-    val_rec = [52.4,61.0,53.3,50.5,47.6]
+    models_directories=["cosface/cosface_best_model.pth","sphereface/sphereface_best_model.pth", "arcface/arcface_best_model.pth"]
+    val_rec = [52.2,49.7,49.7]
     models_list = []
     for idx, model_path in enumerate(models_directories):
         m = load_model(base_path.format(model_path),args)

### 2023-01-31 model_soup.py
fix: update model_soup with all models

@@ -22,9 +22,9 @@ def greedy_soup(models_list, val_folder, args):
         model = model.eval()
        
         sorted_models.append((model, val))
+        continue
         recalls, recalls_str = test.test(args, val_ds, model)
         print(recalls)
-        #continue
 
     sorted_models.sort(key=compare, reverse=True)
     greedy_soup_ingredients = [sorted_models[0][0]]
@@ -73,10 +73,11 @@ if __name__ == "__main__":
     args = parser.parse_arguments(is_training=False)
 
     base_path = "model/{}"
-    models_directories=["cosface/cosface_best_model.pth","sphereface/sphereface_best_model.pth", "arcface/arcface_best_model.pth"]
-    val_rec = [52.2,49.7,49.7]
+    models_directories=["cosface/cosface_best_model.pth","ablation_augmentation/all_models.pth","ablation_augmentation/base_models.pth","ablation_augmentation/erasing_full.pth","ablation_augmentation/gblur_model.pth","ablation_augmentation/gblur_occlusion_full.pth","ablation_augmentation/grayscale_gblur.pth","ablation_augmentation/grayscale_model.pth","ablation_augmentation/grayscale_occlusion_model.pth","ablation_augmentation/hflip_model.pth","ablation_augmentation/occlusion_model.pth"]
+    # val_rec = [52.2,49.7,49.7]
+    val_ds = TestDataset(args.val_set_folder, positive_dist_threshold=args.positive_dist_threshold)
     models_list = []
     for idx, model_path in enumerate(models_directories):
         m = load_model(base_path.format(model_path),args)
-        models_list.append((m, val_rec[idx]))
+        models_list.append((m, val_ds[idx]))
     greedy_soup(models_list, "/content/small/test/", args)

### 2023-01-31 model_soup.py
fix: added all augmentation models

@@ -22,9 +22,10 @@ def greedy_soup(models_list, val_folder, args):
         model = model.eval()
        
         sorted_models.append((model, val))
-        continue
         recalls, recalls_str = test.test(args, val_ds, model)
-        print(recalls)
+        print("model tested: ", model)
+        print("recalls: ", recalls)
+        # continue
 
     sorted_models.sort(key=compare, reverse=True)
     greedy_soup_ingredients = [sorted_models[0][0]]
@@ -73,11 +74,10 @@ if __name__ == "__main__":
     args = parser.parse_arguments(is_training=False)
 
     base_path = "model/{}"
-    models_directories=["cosface/cosface_best_model.pth","ablation_augmentation/all_models.pth","ablation_augmentation/base_models.pth","ablation_augmentation/erasing_full.pth","ablation_augmentation/gblur_model.pth","ablation_augmentation/gblur_occlusion_full.pth","ablation_augmentation/grayscale_gblur.pth","ablation_augmentation/grayscale_model.pth","ablation_augmentation/grayscale_occlusion_model.pth","ablation_augmentation/hflip_model.pth","ablation_augmentation/occlusion_model.pth"]
-    # val_rec = [52.2,49.7,49.7]
-    val_ds = TestDataset(args.val_set_folder, positive_dist_threshold=args.positive_dist_threshold)
+    models_directories=["ablation_augmentation/base_model.pth","ablation_augmentation/gblur_model.pth","ablation_augmentation/grayscale_model.pth","ablation_augmentation/hflip_model.pth","ablation_augmentation/occlusion_model.pth","ablation_augmentation/grayscale_occlusion_model.pth","ablation_augmentation/grayscale_gblur.pth","ablation_augmentation/gblur_occlusion_full.pth","ablation_augmentation/all_models.pth"]
+    val_rec = [1.0, 1.2, 1.2, 1.0, 1.2, 1.1, 1.1, 1.2, 1.0]
     models_list = []
     for idx, model_path in enumerate(models_directories):
         m = load_model(base_path.format(model_path),args)
-        models_list.append((m, val_ds[idx]))
+        models_list.append((m, val_rec[idx]))
     greedy_soup(models_list, "/content/small/test/", args)

### 2023-01-31 model_soup.py
fix: remove print(model)

@@ -23,7 +23,6 @@ def greedy_soup(models_list, val_folder, args):
        
         sorted_models.append((model, val))
         recalls, recalls_str = test.test(args, val_ds, model)
-        print("model tested: ", model)
         print("recalls: ", recalls)
         # continue
 

### 2023-01-31 model_soup.py
fix: remove recallls from every model

@@ -22,9 +22,9 @@ def greedy_soup(models_list, val_folder, args):
         model = model.eval()
        
         sorted_models.append((model, val))
+        continue
         recalls, recalls_str = test.test(args, val_ds, model)
         print("recalls: ", recalls)
-        # continue
 
     sorted_models.sort(key=compare, reverse=True)
     greedy_soup_ingredients = [sorted_models[0][0]]

### 2023-02-01 model_soup.py
parser warning fix

@@ -3,7 +3,7 @@ import test
 from model import network
 import torch
 from datetime import datetime
-import parser
+import our_parser
 
 def load_model(model_path,args):
     model = network.GeoLocalizationNet(args.backbone, args.fc_output_dim)
@@ -70,7 +70,7 @@ def delete_discriminator_layer(model):
 
 if __name__ == "__main__":
 
-    args = parser.parse_arguments(is_training=False)
+    args = our_parser.parse_arguments(is_training=False)
 
     base_path = "model/{}"
     models_directories=["ablation_augmentation/base_model.pth","ablation_augmentation/gblur_model.pth","ablation_augmentation/grayscale_model.pth","ablation_augmentation/hflip_model.pth","ablation_augmentation/occlusion_model.pth","ablation_augmentation/grayscale_occlusion_model.pth","ablation_augmentation/grayscale_gblur.pth","ablation_augmentation/gblur_occlusion_full.pth","ablation_augmentation/all_models.pth"]

### 2023-02-01 our_parser.py

@@ -63,6 +63,8 @@ def parse_arguments(is_training: bool = True):
                         help="path where best_model.pth file is")                      
     # Loss parameters
     parser.add_argument("--loss_function", type=str, default="cosface", choices=["cosface", "sphereface", "arcface", "new_cosface"], help="select which loss to use [cosface, sphereface, arcface, new_cosface]")
+    # GRL parameters
+    parser.add_argument("--grl", type=bool, default=False, choices=[True, False], help="insert --grl True if you want to perform Domain Adaptation")
     
     args = parser.parse_args()
     

### 2023-02-01 train.py

@@ -1,4 +1,3 @@
-
 import sys
 import torch
 import logging
@@ -10,7 +9,7 @@ import torchvision.transforms as T
 
 import test
 import util
-import parser
+import our_parser
 import commons
 import cosface_loss
 import new_cosface_loss
@@ -23,7 +22,7 @@ from datasets.train_dataset import TrainDataset
 
 torch.backends.cudnn.benchmark = True  # Provides a speedup
 
-args = parser.parse_arguments()
+args = our_parser.parse_arguments()
 start_time = datetime.now()
 output_folder = f"logs/{args.save_dir}/{start_time.strftime('%Y-%m-%d_%H-%M-%S')}"
 commons.make_deterministic(args.seed)

### 2023-02-01 test_only.py
GRL implementation added

@@ -10,7 +10,7 @@ import torchvision.transforms as T
 
 import test
 import util
-import parser
+import our_parser
 import commons
 import cosface_loss
 import augmentations
@@ -20,7 +20,7 @@ from datasets.train_dataset import TrainDataset
 
 torch.backends.cudnn.benchmark = True  # Provides a speedup
 
-args = parser.parse_arguments(is_training=False)
+args = our_parser.parse_arguments(is_training=False)
 start_time = datetime.now()
 output_folder = f"logs/{args.save_dir}/{start_time.strftime('%Y-%m-%d_%H-%M-%S')}"
 best_model = args.best_model #path to best model: "AML23-Cosplace/model/results/best_..."
@@ -33,6 +33,7 @@ logging.info(f"The outputs are being saved in {output_folder}")
 #### Model
 model = network.GeoLocalizationNet(args.backbone, args.fc_output_dim)
 
+
 model = model.to(args.device).train()
 
 
@@ -42,6 +43,15 @@ logging.info(f"Test set: {test_ds}")
 
 #### Test best model on test set
 best_model_state_dict = torch.load(best_model)
+
+if args.grl == True:
+        del best_model_state_dict["domain_discriminator.1.weight"]
+        del best_model_state_dict["domain_discriminator.1.bias"]
+        del best_model_state_dict["domain_discriminator.3.weight"]
+        del best_model_state_dict["domain_discriminator.3.bias"]
+        del best_model_state_dict["domain_discriminator.5.weight"]
+        del best_model_state_dict["domain_discriminator.5.bias"]
+        
 model.load_state_dict(best_model_state_dict)
 
 logging.info(f"Now testing on the test set: {test_ds}")

### 2023-02-01 train_only.py

@@ -10,7 +10,7 @@ import torchvision.transforms as T
 import custom_augmentations as CA
 import test
 import util
-import parser
+import our_parser
 import commons
 import cosface_loss
 import new_cosface_loss
@@ -20,11 +20,12 @@ import augmentations
 from model import network
 from datasets.test_dataset import TestDataset
 from datasets.train_dataset import TrainDataset
+from datasets.grl_datasets import GrlDataset
 import random 
 
 torch.backends.cudnn.benchmark = True  # Provides a speedup
 
-args = parser.parse_arguments()
+args = our_parser.parse_arguments()
 start_time = datetime.now()
 output_folder = f"AML23-CosPlace/model/results/best_{start_time.strftime('%Y-%m-%d_%H-%M-%S')}"
 commons.make_deterministic(args.seed)
@@ -33,8 +34,8 @@ logging.info(" ".join(sys.argv))
 logging.info(f"Arguments: {args}")
 logging.info(f"The outputs are being saved in {output_folder}")
 
-#### Model
-model = network.GeoLocalizationNet(args.backbone, args.fc_output_dim)
+#### Model (+ GRL for domain adaptation)
+model = network.GeoLocalizationNet(args.backbone, args.fc_output_dim, grl = args.grl)
 
 logging.info(f"There are {torch.cuda.device_count()} GPUs and {multiprocessing.cpu_count()} CPUs.")
 
@@ -47,11 +48,15 @@ model = model.to(args.device).train()
 
 #### Optimizer
 criterion = torch.nn.CrossEntropyLoss()
+epoch_grl_loss = 0 
+domain_adapt_criterion = torch.nn.CrossEntropyLoss() if args.grl == True else None #Loss for Domain Adaptation
 model_optimizer = torch.optim.Adam(model.parameters(), lr=args.lr)
 
 #### Datasets
 groups = [TrainDataset(args, args.train_set_folder, M=args.M, alpha=args.alpha, N=args.N, L=args.L,
                        current_group=n, min_images_per_class=args.min_images_per_class) for n in range(args.groups_num)]
+grl_dataset = GrlDataset(sf_xs_train_path="/content/small/train", target_path="/content/AML23-CosPlace/our_FDA/target") if args.grl == True else None #To Do... Add Target Dataset for Domain Adaptation
+
 # Each group has its own classifier, which depends on the number of classes in the group
 # Each group has its own classifier, which depends on the number of classes in the group
[…]

### 2023-02-02 GRL/GRL.py
grl clean and small fix

@@ -1,9 +1,5 @@
-import glob
-import random
-import logging
 import torch
 import torch.nn as nn
-from PIL import Image
 import torchvision.transforms as transforms
 
 '''
@@ -49,33 +45,4 @@ grl_transform = transforms.Compose([
             transforms.ToTensor(),
             transforms.Normalize(mean=[0.485, 0.456, 0.406], std=[0.229, 0.224, 0.225]),
     ])
-
-class GrlDataset(torch.utils.data.Dataset):
-    def __init__(self, dataset_root, datasets_paths, length=1000000):
-        """
-        datasets_paths is a list containing the folders which contain the N datasets.
-        __len__() returns 1000000, and __getitem__(index) returns a random
-        image, from dataset index % N, to ensure that each dataset has the 
-        same chance of being picked
-        """
-        super().__init__()
-        self.num_classes = len(datasets_paths)
-        logging.info(f"GrlDataset has {self.num_classes} classes")
-        self.images_paths = []
-        for dataset_path in datasets_paths:
-            self.images_paths.append(sorted(glob.glob(f"{dataset_root}/{dataset_path}/**/*.jpg", recursive=True)))
-            logging.info(f"    Class {dataset_path} has {len(self.images_paths[-1])} images")
-            if len(self.images_paths[-1]) == 0:
-                raise Exception(f"Class {dataset_path} has 0 images, that's a problem!!!")
-        self.transform = grl_transform
-        self.length = length
-    def __getitem__(self, index):
-        num_class = index % self.num_classes
-        images_of_class = self.images_paths[num_class]
-        # choose a random one
-        image_path = random.choice(images_of_class)
-        tensor = self.transform(Image.open(image_path).convert("RGB"))
-        return tensor, num_class
-    def __len__(self):
-        return self.length
 

### 2023-02-02 train_only.py

@@ -134,7 +134,7 @@ for epoch_num in range(start_epoch_num, args.epochs_num):
                                             pin_memory=(args.device == "cuda"), drop_last=True) if args.grl == True else None
     
     dataloader_iterator = iter(dataloader)
-    domain_adapt_dataloader_iterator = iter(domain_adapt_dataloader)
+    domain_adapt_dataloader_iterator = iter(domain_adapt_dataloader) if args.grl == True else None
     model = model.train()
     
     epoch_losses = np.zeros((0, 1), dtype=np.float32)

### 2023-02-03 our_parser.py
Set custom augmentation to 0

@@ -34,10 +34,10 @@ def parse_arguments(is_training: bool = True):
     parser.add_argument("--saturation", type=float, default=0.7, help="_")
     parser.add_argument("--random_resized_crop", type=float, default=0.5, help="_")
     #custom agumentations
-    parser.add_argument("--hflip", type=float, default=0.25, help="_")
-    parser.add_argument("--gblur", type=float, default=0.25, help="_")
-    parser.add_argument("--rgrayscale", type=float, default=0.25, help="_")
-    parser.add_argument("--rerasing", type=float, default=0.25, help="_")
+    parser.add_argument("--hflip", type=float, default=0, help="_")
+    parser.add_argument("--gblur", type=float, default=0, help="_")
+    parser.add_argument("--rgrayscale", type=float, default=0, help="_")
+    parser.add_argument("--rerasing", type=float, default=0, help="_")
 
     # Validation / test parameters
     parser.add_argument("--infer_batch_size", type=int, default=16,

### 2023-02-03 paper/paper.tex
added paper latest version

--- 2023-01-28 paper/paper.tex
@@
 %%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
-\usepackage[review]{cvpr}      % To produce the REVIEW version
+%\usepackage[review]{cvpr}      % To produce the REVIEW version
 %\usepackage{cvpr}              % To produce the CAMERA-READY version
-%\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version
+\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version
 
@@
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{Visual Geolocalization:
+\title{Visual Geo-Localization:
 mapping images to GPS}
 
-\author{Testa Mario\\
-PoliTo\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
+\author{Cambria Paolo - s301164\\
+Politecnico di Torino\\
+{\tt\small paolocambria@studenti.polito.it}
 \and
-Cambria Paolo\\
-PoliTo\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
+Ciciriello Giuseppe - s301953\\
+Politecnico di Torino\\
+{\tt\small giuseppe.ciciriello@studenti.polito.it}
 \and
-Ciciriello Giuseppe\\
-PoliTo\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
+Testa Mario - s292630\\
+Politecnico di Torino\\
+{\tt\small mario.testa@studenti.polito.it}
 }
+
 \maketitle
@@
 \begin{abstract}
-In this work, we develop a theoretical and experimental framework to study the effect of CosFace loss function to localize unseen images.
-Our theory extract the N-top retrieved images, with their geo-tag, the retrieval is performed as a k-Nearest Neighbour search.
-Finally, we conduct a thorough ablation study of the loss function by changing it with SphereFace and ArcFace loss functions.
-We then conducted experiments on image recognition benchmarks.
-%   The ABSTRACT is to be in fully justified italicized text, at the top of the left-hand column, below the author and affiliation information.
-%   Use the word ``Abstract'' as the title, in 12-point Times, boldface type, centered relative to the column, initially capitalized.
-%   The abstract is to be in 10-point, single-spaced type.
-%   Leave two blank lines after the Abstract, then begin the main text.
-%   Look at previous CVPR abstracts to get a feel for style and length.
+Visual Geo-localization (VG) is the task of estimating the position where a given photo was taken by comparing it with a large database of images of known locations.
+In this work, we investigate the results of CosPlace~\cite{Berton_CVPR_2022_CosPlace} in the task of Visual Geo-Localization.
+Their method casts the training as a classification problem and achieves state-of-the-art performances on a wide range of datasets and domain changes.
+We conducted a thorough ablation study of the loss function by comparing it with SphereFace and ArcFace loss functions and, finally, we carried out experiments on Domain Adaptation and Model Ensemble to try reach better benchmarks.
+[TODO REVIEW FINALE]
+Dataset, code and trained models are available for research purposes at: \newline
+\url{https://github.com/Spidersaw/AML23-CosPlace/}
 \end{abstract}
@@
 %%%%%%%%% BODY TEXT
-\section{Introduction}
-\label{sec:intro}
+\section{Introduction}\label{sec:introduction}
+Visual geo-localization (VG) is one of the most promising approaches in the field of computer vision and image localization,
+due to his importance in applications such as autonomous driving~\cite{6906961} or even augmented reality~\cite{middelberg}.
+VG usually consists of a place recognition task: given a query image of a place, its geographical location has to be roughly recognized and retrieved
+by finding the closest database geo-tagged images usually with a tolerance of few meters. 
+This task is extremely challenging due to the intrinsic dynamism of public places and different problems must be taken in account:
+there are a lot of moving objects which determine occlusion, environmental changes, different illuminations during daylight and night time, season changing.
+Furthermore, most of the recent learning based VG methods focus on recognizing the location of images in a relatively small sized geographical area (\eg a neighborhood), 
+which is not enough for real-world applications which are posed to operate at much larger scale (\eg whole cities).
+\newline
+\textbf{Non-representative datasets.}
+To achieve a VG task on a wider geographical area, a large representative dataset is required and, as underlined by~\cite{Berton_CVPR_2022_CosPlace}, the majority of 
+current datasets are either too small in the geographical coverage~\cite{netvlad,lidards,kittids}, or too sparse \cite{oxfds, mapillary}. Moreover, those datasets split the collected images into 
+disjoint sets for training and inference and this not suits a realistic use case, since the search query might be often an already seen place.
+For this reason it is recommendable to use the whole dataset to train the model, given also the cost of collecting the images for a consistent dataset.
+\newline
+\textbf{Training scalability}
+Having access to a massive amount of data raises the question of how to use it effectively for training. Many of the recent SOTA (state-of-the-art) methods take advantage
+of contrastive learning ~\cite{netvlad, adageo}, which can often depend on contrasting positive to negative examples across the training dataset, a costly operation in terms of computation.
+CosPlace~\cite{Berton_CVPR_2022_CosPlace}, instead, addresses this limitation by using:
+\begin{itemize}
+    \item a new large-scale and dense dataset, called San Francisco eXtra Large (SF-XL), which includes multi-domain queries.
+    \item a highly scalable training method, properly designed to work on large dataset, based on a classification task to produce a model that will later be used to extract descriptors for the retrieval
+\end{itemize}
+successfully reaching SOTA results with compact descriptors.
+\newline
+\textbf{Contributions}
+In this paper we want to investigate how the work of~\cite{Berton_CVPR_2022_CosPlace} can be improved for place recognition tasks, but using a smaller version of SF-XL dataset (called SF-XS) for the training, due to our limited resources.
+In particular we focus on trying to:
+\begin{itemize}
+    \item generally improve the recalls on SF-XS and Tokyo-XS (a smaller version of Tokyo 24/7~\cite{tokyo247}), even with the help of ensembles to concatenate the descriptors of different models.
+    \item improve robustness to domain shift by borrowing techniques from the field of domain adaptation~\cite{adageo}, and testing the results on a dataset which only contains night images, called Tokyo-Night (a filtered version of Tokyo-XS).
+    \item assess how CosPlace behaves when data quality is scarce (\eg occlusion and blurry photos). 
+\end{itemize}
 
-Please follow the steps outlined below when submitting your manuscript to the IEEE Computer Society Press.
-This style guide now has several important modifications (for example, you are no longer warned against the use of sticky tape to attach your artwork to the paper), so all authors should read this new version.
+[TODO conclusioni rapide]
 
 %-------------------------------------------------------------------------
-\subsection{Language}
 
-All manuscripts must be in English.
-
-\subsection{Dual submission}
-
-Please refer to the author guidelines on the \confName\ \confYear\ web page for a
-discussion of the policy on dual submissions.
-
-\subsection{Paper length}
-Papers, excluding the references section, must be no longer than eight pages in length.
-The references section will not be included in the page count, and there is no limit on the length of the references section.
-For example, a paper of eight pages with two pages of references would have a total length of 10 pages.
-{\bf There will be no extra page charges for \confName\ \confYear.}
-
-Overlength papers will simply not be reviewed.
-This includes papers where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
-Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.
-The reason such papers will not be reviewed is that there is no provision for supervised revisions of manuscripts.
-The reviewing process cannot determine the suitability of the paper for presentation in eight pages if it is reviewed in eleven.
+\begin{figure*}
+  \centering
+  \begin{subfigure}{1.0\linewidth}
+    \centering
+    \fbox{ \includegraphics[width=\dimexpr\textwidth-2\fboxrule-2\fboxsep]{assets/architecture.png}}
+    \caption{The proposed architecture.
+First, a domain-driven data augmentation method is used to generate a labeled pseudo-target dataset from the source dataset and just 5 unlabeled target images.
+Then, the source dataset, pseudo-target dataset, and the 5 unlabeled target images are used to train the network that extracts the image descriptors.
+This network leverages an aggregation module and a domain adaptation module to provide robustness to shifting.}
+    \label{fig:our_architecture}
+  \end{subfigure}
+  \hfill
+\end{figure*}
 
 %-------------------------------------------------------------------------
+\section{Related Works}\label{sec:relatedworks}
+\textbf{Visual geo-localization as image retrieval.} Visual geolocalization on large scale is commonly considered as an image retrieval task, in which the correctness is determined by an established
+tolerance (usually 25 meters) from the query's ground truth position~\cite{netvlad, adageo}.    
+One of the most representative study in this field is NetVLAD~\cite{netvlad}, which introduces a VLAD layer, which has parameters learnable with back-propagation, that pools descriptors extracted from a CNN backbone into a fixed image representation.
+\newline
+\textbf{Visual geo-localization as classification.}
+An alternative approach to visual geo-localization is to consider it a classification problem, as done in~\cite{Berton_CVPR_2022_CosPlace}.
+Most of methods of this kind, divide the geographical area of interest in cells and group the database of images in classes according to their cell, which has a big limitation: nearly identical images may be assigned to different classes due to quantization errors.
+CosPlace, instead, proposes to train the model only using groups of non adjacent classes and iterates over them while using CosFace~\cite{cosface} as a scalable loss.
+\newline
+\textbf{Deep Face Recognition.}
+In deep face recognition (FR) problem under open-set protocol, ideal face features are expected to have smaller maximal intra-class distance than minimal inter-class distance under a suitably chosen metric space.
+Different methods~\cite{sphereface, cosface, arcface} have shown how learning angularly discriminative features on a hypersphere manifold with an adjustable margin helps to improve accuracy on both verification and identification tasks.
+The most representative studies in this field are SphereFace~\cite{sphereface} which uses a multiplicative angular margin inside the loss function, CosFace~\cite{cosface} which applies an additive cosine margin directly to the target logits and ArcFace~\cite{arcface} which applies an angular margin that exactly corresponds to the geodesic distance.
+[TODO Non mi piace tanto com'è scritta la descrizione di sphere, cos e arc...]
+\newline
+\textbf{Unsupervised domain adaptation.}
+Unsupervised domain adaptation attempts to reduce the shift between the source and target distribution of the data by relying only on labeled source data and unlabeled target data.
+For example, the source domain can consist of synthetic images and their corresponding pixel-level labels (\eg for semantic segmentation), and the target can be real images with no ground-truth annotations.
+One approach for unsupervised domain adaptation is to learn domain-invariant features from the data, it was introduced by~\cite{grl} and is based on a domain discriminator network with a gradient reversal layer (GRL) that forces feature extractor to produce domain-invariant representations.
+This has been used by AdaGeo-Lite~\cite{adageo} architecture, which combines a domain-driven data augmentation module that uses a non-learned style transfer method (called FDA~\cite{fda}) producing a pseudo-target labeled dataset, with a network that produces domain-invariant image descriptors by setting up a min-max game where the discriminator tries to minimize the domain classification loss given three datasets (source, pseudo-target and a few samples from the target domain), while the feature extractor acts as an adversary to the discriminator.
+%-------------------------------------------------------------------------
+\section{Method}\label{sec:experiments}
+In this section, we present different approaches we have used to try improving CosPlace results.
+We started from its original implementation and decided to add custom augmentation to help boost its ability to learn embeddings even on sub-optimal picture quality.
+Then, we moved our focus to domain shift, given that test-images are likely to come from different domains than the source and that the domain shift in the dataset of interest Tokyo-Night is caused by illumination (day/night), we tried adapting the method used by~\cite{adageo} combined to CosPlace in order to create a modular architecture composed of two parts:
+\begin{itemize}
+    \item A non-learned domain-driven data augmentation module that transfer the style of the target domain (night) to the source images.
+    \item A network that produces the image descriptors, composed of a CNN, an aggregation layer and domain adaptation module.
+\end{itemize}
+At the end, we tried averaging the weights of models trained in the previous steps using Model Soups' approach~\cite{modelsoup} to improve recalls.
+\subsection{CosPlace}
+Our work starts from CosPlace, an innovative approach in the field of visual geo-localization~\cite{Berton_CVPR_2022_CosPlace}.
+CosPlace casts the network training as an image classification problem: it partition the geographical area of interest in oriented cells, representing different classes, using UTM coordinates $\{east,north\}$\footnote{UTM coordinates are defined by a system used to identify locations on earth in meters, where 1 UTM unit corresponds to 1 meter.
+They can be extracted from GPS coordinates (i.e., latitude and longitude) and allow approximating a restricted area of the earth’s surface on a flat surface.} and orientation/heading $\{heading\}$.
+The extent of each class in terms of position and heading is defined by two parameters $M$ and $\alpha$, respectively.
+Then, it iteratively considers subsets of these cells (called groups $G_{uvw}$) to train the network.
+These groups are generated by fixing the minimum spatial separation that two classes of the same group should have, either in terms of translation or orientation.
+For this reason, they introduced two parameters: $N$ controls the minimum number of cells between two classes of the same group, and $L$ is the equivalent for the orientation.
+Therefore, we have trained sequentially over the groups as:
+\begin{equation}
+  \mathcal{L}_{cosPlace} = \mathcal{L}_{lmcl}(G_{uvw})
+  \label{eq:cosplace_full}
+\end{equation}
+where $\mathcal{L}_{lmcl}$ is the Large Margin Cosine Loss as defined in~\cite{cosface}, and $u \in \{0,...,N\}, v \in \{0,...,N\}, w \in \{0,...,L\}$ represent the different values of $\{east, north, heading\}$.
+In our case, due to limitations in compute availability, we could only train each epoch on the same group $G$, so:
+\begin{equation}
+  \mathcal{L}_{cosPlace} = \mathcal{L}_{lmcl}(G)
+  \label{eq:cosplace_our}
+\end{equation}
+At validation and test time, we used the model generated not to classify the query, but rather to extract image descriptors as in~\cite{cosface} for a classic retrieval over the database.
+This allows for the model to be used also on other datasets from unseen geographical areas, like Tokyo-XS and the smaller Tokyo-Night.
+\subsection{Custom Augmentations}
+To assess the robustness of CosPlace~\cite{Berton_CVPR_2022_CosPlace} and improve its capability to learn a good embedding space even on sub-optimal picture quality we conducted a study on the augmentation pipeline already present in the original implementation (Color Jitter, RandomResizedCrop, Normalize) that we named \textbf{base} for our ablation, by adding 4 new augmentations on the images with a probability of 25\% and a fixed seed for reproducibility purposes.
+Those augmentations consisted of:
+\begin{itemize}
+  \item Gaussian Blur
+  \item Gray scale
+  \item Horizontal Flip
+  \item Erasing
+\end{itemize}
+[TODO] Insert here description of the custom augmentations made, how they were implemented, citing where inspiration was taken.
+\subsection{FDA and GRL}
+\textbf{FDA}
+The purpose of the domain-driven data augmentation (DDDA) module is to find a mapping $D_s \mapsto D_{pt}$ from the source domain to a pseudo-target domain that better approximates the target domain, i.e., $D_{pt} \approx D_t$.
+This mapping can then be applied to the source dataset $X_s$ to generate a new labeled dataset with pseudo-target images $X_{pt}$, it is a data augmentation technique and is performed only once, offline.
+Inspired by~\cite{fda, adageo}, we propose a DDDA method based on Fourier Domain Adaptation (FDA) to generate a pseudo-target dataset $X_{pt}$ given two randomly sampled images $x^s$ and $x^t$ from source and target.
+First, the low frequency part of the amplitude of $x^s$ is replaced by that of $x^t$, then the modified spectral representation of the source is mapped back to an image whose content is the same as $x^s$ but will resemble the appearance of a sample from the target distribution.
+\newline
+Afterward, we use both $X_s$ and $X_{pt}$ to train the descriptor extraction network, leading to a more robust model.
+In order for the retrieval to work well across domains it is important that the embeddings produced by the descriptor extraction network are domain agnostic, i.e., they do not encode domain-specific information.
+We achieve this by using a domain discriminator which receives embeddings from the three domains $D_s$, $D_pt$, and $D_t$.
+The discriminator is composed of two fully connected layers, and its goal is to classify the domain to which the embeddings belong.
+Just before the discriminator, there is a gradient reversal layer (Ganin and Lempitsky, 2015) that in the forward pass acts as an identity transform, while in the backward pass multiplies the gradient by -$\lambda$, where $\lambda > 0$.
+The use of this layer effectively sets up a min-max game, where the discriminator tries to minimize the domain classification loss, that is a cross-entropy loss $L_{CE}$, while the feature extractor learns to produce domain-invariant embeddings, acting as an adversary to the discriminator.
+
+\textbf{GRL.} We define a deep feed-forward architecture that for each input $x$ predicts its class $y \in Y$ and its domain label $d \in \{0, 1\}$, depending if it is an image from day or night.
+[TODO] To finish...
+
+\subsection{Model Soup}
+[TODO] Insert here description of how Model Soup has been implemented.
+
+\section{Experiments}
+\textbf{Experiment with the Baseline.}
+We started running some experiments to better understand how the training procedure worked.
+The backbone used was a ResNet-18 pre-trained on ImageNet with GeM pooling~\cite{finetuning} and due to limitations in compute availability (\eg Colab time and GPU limitations), we trained the baseline model for only 3 epochs to finally end up with the results in \cref{tab:baseline}:
+
+\begin{table}[htp]
+  \centering
+  \begin{tabular}{@{}cccc@{}}
+    \toprule
+    & SF-XS(test) & Tokyo-XS & Tokyo-Night\\
+    \midrule
+    R@1/R@5 & \textbf{52.2/66.3} & \textbf{69.5/84.8} & \textbf{49.5/72.4} \\
+    R@10 & 71.8 & 89.2 & 79.0\\
+    R@20 & 76.3 & 92.7 & 84.4\\
+    \bottomrule
+  \end{tabular}
+  \caption{Baseline results, values refer to recall@K, for K=\{1, 5, 10, 20\}}
+  \label{tab:baseline}
+\end{table}
+
+\textbf{Ablation study when changing the angular loss function.}
+Once we were familiar with the baseline, we started making a few modifications to the model, specifically to the loss function.
+Standard CosPlace uses the Large Cosine similarity loss~\cite{cosface}, so we've tried replacing it with two other alternative cosine based losses: SphereFace~\cite{sphereface} and ArcFace~\cite{arcface}.
+We trained the modified version on SF-XS and the results in \cref{tab:lossablation} show how CosFace loss performs better than the competition on the biggest dataset (SF-XS), while on smaller ones (Tokyo-XS and Tokyo-Night) SphereFace and ArcFace actually get better recall values.
+This isn't what we expected at first, but further analysis suggest us that the implementations we've use for the last two losses might converge earlier than the original CosFace, so with a low number of epochs they perform better.
+It would be interesting to have some trials with the full SF-XL dataset and a greater number of epochs to better understand the behavior in the long run.
+
+\begin{table}[htp]
+  \centering
+  \begin{tabular}{@{}cccc@{}}
+    \toprule
+     & SF-XS(test) & Tokyo-XS & Tokyo-Night\\
+    \midrule
+    CosPlace with\\ CosFace & \textbf{52.2/66.3} & 69.5/84.8 & 49.5/72.4 \\
+    CosPlace with\\ SphereFace & 49.7/64.2 & \textbf{70.2/84.8} & \textbf{59.0/75.2} \\
+    CosPlace with\\ ArcFace & 49.7/61.1 & 69.5/81.6 & 56.2/64.8\\
+    \bottomrule
+  \end{tabular}
+  \caption{Results of our ablation study when changing the angular loss function from CosFace to SphereFace and ArcFace, the values refer to Recall@1/Recall@5.}
+  \label{tab:lossablation}
+\end{table}
+
+\textbf{Augmentation Pipeline.}
+Due to the high computational requirements, we were only able to conduct this ablation efficiently on SF-XS dataset with a low amount of iterations per epochs fixed to 5000.
+The results reporting recalls are reported in the table \ref{tab:augmentations-pp} below:
+
+% ABLATION AUGMENTATIONS
+
+\begin{table}[hbp] % Add the following just after the closing bracket on this line to specify a position for the table on the page: [h], [t], [b] or [p] - these mean: here, top, bottom and on a separate page, respectively
+\centering % Centers the table on the page, comment out to left-justify
+\begin{tabular}{l c c c c c} % The final bracket specifies the number of columns in the table along with left and right borders which are specified using vertical bars (|); each column can be left, right or center-justified using l, r or c.
+To specify a precise width, use p{width}, e.g.
+p{5cm}
+\toprule % Top horizontal line
+Augmentations & R@1 & R@5 & R@10 & R@20\\ % Column names row
+\midrule % In-table horizontal line
+Base & 1.0\%  & 1.6\% & 1.9\% & 2.0\%  \\ 
++\{blur\} & 1.2\%  & 1.8\% & 2.0\% & 2.0\%  \\ 
++\{grayscale\} & 1.2\%  & 1.7\% & 1.9\% & 2.0\%  \\ 
++\{flip\} & 1.0\%  & 1.7\% & 1.8\% & 1.9\%  \\  
++\{erasing\} & 1.2\%  & 1.9\% & 1.9\% & 1.9\%  \\  
++\{grayscale, erasing\} & 1.1\%  & 1.9\% & 1.9\% & 2.0\%  \\  
++\{blur, grayscale\} & 1.1\%  & 1.9\% & 2.0\% & 2.0\%  \\  
++\{\textbf{blur, erasing}\} & 1.2\%  & 1.9\% & 2.0\% & 2.0\%  \\  
++\{blur, grayscale,\\ flip, erasing\} & 1.0\%  & 1.7\% & 2.0\% & 2.0\%  \\
+
+\bottomrule % Bottom horizontal line
+\end{tabular}
+\smallskip 
+\caption{Evaluation of the impact in terms of recall of different augmentation pipelines for CosPlace compared to Base (Color Jitter, RandomResizedCrop, Normalize)
+} % Table caption, can be commented out if no caption is required
+\label{tab:augmentations-pp} % A label for referencing this table elsewhere, references are used in text as \ref{label}
+\end{table}
+
+The couple \textbf{blur, erasing} seems the best choice for the augmentation pipeline, since not only the model manages to show robustness to that data augmentation pipeline, but also improves.
+However, further investigations should be performed with a larger amount of data and a higher amount of iterations to understand if this is an improvement linked to a better generalization due to the lack of data.
+[TODO guardare extension b]
+\newline
+
+\textbf{Unsupervised Domain Adaptation with FDA and GRL.}
+To evaluate the capability of our solution to generalize to unseen domains, specifically the night one, we compare the baseline, the unchanged architecture of the baseline trained with a dataset containing the source domain samples and target-domain samples generated with FDA, and the architecture with the domain discriminator module attached (FDA+GRL).
+In \cref{tab:fda+grl} we show the results for each method.
+
+\begin{table}[htp]
+  \centering
+  \begin{tabular}{@{}cccc@{}}
+    \toprule
+    & SF-XS(test) & Tokyo-XS & Tokyo-Night\\
+    \midrule
+    Baseline & 52.2/66.3 & 69.5/84.8 & 49.5/72.4 \\
+    FDA & 50.5/65.4 & 67.0/85.7 & 47.6/72.4 \\
+    FDA+GRL & \textbf{53.7/66.5} & \textbf{70.5/84.8} & \textbf{53.3/73.3}\\
+    \bottomrule
+  \end{tabular}
+  \caption{Baseline results compared with FDA only and FDA+GRL (with $\alpha=0.1$)}
+  \label{tab:fda+grl}
+\end{table}
+
+From these results, we surpass the baseline in all the three datasets by using both FDA and GRL together, reaching a \~4\% improvement on Tokyo-night.
+This confirms that the newly generated model was able to produce "more" domain-invariant features than before.
+Better can be expected, as the shift between this domain and the source domain (StreetView) is extreme, with very dark images and with a strong yellow tones.
+
+\section{Conclusions}
+[TODO] Insert here conclusions and possible further implementations.
+
+\section{Stuff to copy for Latex}
+
 \subsection{The ruler}

### 2023-02-03 paper/paper.tex
paper updated

@@
 \textbf{Augmentation Pipeline.}
-Due to the high computational requirements, we were only able to conduct this ablation efficiently on SF-XS dataset with a low amount of iterations per epochs fixed to 5000.
-The results reporting recalls are reported in the table \ref{tab:augmentations-pp} below:
+Due to the high computational requirements, we were only able to conduct this ablation efficiently on SF-XS dataset with a low amount of iterations per epochs fixed to 5000 and a batch size reduced to 16 instead of respectively 10000 and 32 as the default model.
+The results reporting recalls are presented in the table \ref{tab:augmentations-pp} below:
 
@@
 \midrule % In-table horizontal line
-Base & 1.0\%  & 1.6\% & 1.9\% & 2.0\%  \\ 
-+\{blur\} & 1.2\%  & 1.8\% & 2.0\% & 2.0\%  \\ 
-+\{grayscale\} & 1.2\%  & 1.7\% & 1.9\% & 2.0\%  \\ 
-+\{flip\} & 1.0\%  & 1.7\% & 1.8\% & 1.9\%  \\  
-+\{erasing\} & 1.2\%  & 1.9\% & 1.9\% & 1.9\%  \\  
-+\{grayscale, erasing\} & 1.1\%  & 1.9\% & 1.9\% & 2.0\%  \\  
-+\{blur, grayscale\} & 1.1\%  & 1.9\% & 2.0\% & 2.0\%  \\  
-+\{\textbf{blur, erasing}\} & 1.2\%  & 1.9\% & 2.0\% & 2.0\%  \\  
-+\{blur, grayscale,\\ flip, erasing\} & 1.0\%  & 1.7\% & 2.0\% & 2.0\%  \\
+Base & 43.9\%  & 61.7\% & 67.0\% & 71.2\%  \\ 
++\{blur\} & 44.2\%  & 60.4\% & 67.3\% & 70.8\%  \\ 
++\{grayscale\} & 45.6\%  & 60.9\% & 67.4\% & 70.7\%  \\ 
++\{flip\} & 43.8\%  & 62.0\% & 68.0\% & 71.9\%  \\  
++\{erasing\} & 44.0\%  & 59.8\% & 65.0\% & 70.2\%  \\  
++\{grayscale, erasing\} & 43.4\%  & 59.2\% & 65.2\% & 70.1\%  \\  
++\{blur, grayscale\} & 45.9\%  & 61.3\% & 68.6\% & 70.9\%  \\  
++\{blur, erasing\} & 43.8\%  & 60.2\% & 65.3\% & 70.4\%  \\  
++\{blur, grayscale,\\ flip, erasing\} & 43.6\%  & 59.1\% & 64.8\% & 70.4\%  \\
 
@@
 
-The couple \textbf{blur, erasing} seems the best choice for the augmentation pipeline, since not only the model manages to show robustness to that data augmentation pipeline, but also improves.
-However, further investigations should be performed with a larger amount of data and a higher amount of iterations to understand if this is an improvement linked to a better generalization due to the lack of data.
+The couple of augmentation \textbf{blur, grayscale} seems the best choice for the augmentation pipeline, since not only the model manages to show robustness to that data augmentation pipeline, but also gets improvements.
+Further investigations should be performed with different parameters to deeply understand those results, however it seems that grayscale performs better since it show invariance to the colors of the scenes changing through the day.
+[TODO valutare se aggiungere ref.]
 [TODO guardare extension b]
@@
 Better can be expected, as the shift between this domain and the source domain (StreetView) is extreme, with very dark images and with a strong yellow tones.
+
+\textbf{Qualitative Evaluation with Top K-NN}
+\newline 
+To assess the goodness of the results obtained applying FDA and GRL in particular on Tokyo-Night dataset, we look at the nearest neighbors in the feature space, to understand the trained model's reasoning on different proposed queries.
+Therefore, we built a top K - Nearest Neighbors visualization
+for which given a query image, the K closest points in the learning embedding space are retrieved.
+In order to retrieve the top K = 5 most similar images to a given one, we calculate the Euclidean distance between the target image's embedding and each image's embedding in the dataset, one by one.
+For our experiment, we used and tested Tokyo-Night [TODO REF] as database for the queries retrieval in fig. \ref{fig:tokyonighttopknn} in two different ways.
+The model was trained with FDA and GRL active [TODO review..], however in the set A)\newline we didn't apply FDA to the images just to be sure that our trained model worked as intended with the original set both on day and night queries and the result was perfect for the first 3 neighbors.
+In the set B) we applied FDA to the dataset and used as query the same image treated with FDA (on the left) and another among its correct night queries (on the right).
+Once again the result was satisfactory and the FDA-treated image was perfectly recognized and integrated in both cases, proving the correct reasoning of our proposed model.
+
+\begin{figure*}
+  \centering
+  \begin{subfigure}{1.0\linewidth}
+    \centering
+    \fbox{ \includegraphics[width=\dimexpr\textwidth-2\fboxrule-2\fboxsep]{assets/topknn.png}}
+    \caption{2a TODO CAPTION, attention to ref}
+    \label{fig:tokyonighttopknn}
+  \end{subfigure}
+  \hfill
+\end{figure*}
 

### 2023-02-04 train_only.py
comments added

@@ -153,9 +153,9 @@ for epoch_num in range(start_epoch_num, args.epochs_num):
         classifiers_optimizers[current_group_num].zero_grad()
         
         if not args.use_amp16:
-            descriptors = model(images)
-            output = classifiers[current_group_num](descriptors, targets)
-            loss = criterion(output, targets)
+            descriptors = model(images) #feature extraction -> theta_f
+            output = classifiers[current_group_num](descriptors, targets) #output probabilities for each class -> theta_y
+            loss = criterion(output, targets) #scalar value that represents the difference between the predicted and true class probabilities.
             loss.backward()
             '''
             Domain Adaptation here
@@ -167,7 +167,7 @@ for epoch_num in range(start_epoch_num, args.epochs_num):
                 domain_adapt_loss = domain_adapt_criterion(domain_adapt_output, domain_adapt_labels)
                 domain_adapt_loss = domain_adapt_loss * alpha
                 domain_adapt_loss.backward()
-                domain_adapt_loss = domain_adapt_loss.item()
+                domain_adapt_loss = domain_adapt_loss.item() #.item() returns tensor value as a standard number
                 epoch_grl_loss += domain_adapt_loss
                 del domain_adapt_images, domain_adapt_output
 

### 2023-02-04 paper/paper.tex
Paper update

@@
 %-------------------------------------------------------------------------
-
-\begin{figure*}
-  \centering
-  \begin{subfigure}{1.0\linewidth}
-    \centering
-    \fbox{ \includegraphics[width=\dimexpr\textwidth-2\fboxrule-2\fboxsep]{assets/architecture.png}}
-    \caption{The proposed architecture.
-First, a domain-driven data augmentation method is used to generate a labeled pseudo-target dataset from the source dataset and just 5 unlabeled target images.
-Then, the source dataset, pseudo-target dataset, and the 5 unlabeled target images are used to train the network that extracts the image descriptors.
-This network leverages an aggregation module and a domain adaptation module to provide robustness to shifting.}
-    \label{fig:our_architecture}
-  \end{subfigure}
-  \hfill
-\end{figure*}
-
-%-------------------------------------------------------------------------
 \section{Related Works}\label{sec:relatedworks}
@@
 \newline
+
 \textbf{Visual geo-localization as classification.}
@@
 \newline
+
 \textbf{Deep Face Recognition.}
@@
 \newline
+
 \textbf{Unsupervised domain adaptation.}
@@
 This has been used by AdaGeo-Lite~\cite{adageo} architecture, which combines a domain-driven data augmentation module that uses a non-learned style transfer method (called FDA~\cite{fda}) producing a pseudo-target labeled dataset, with a network that produces domain-invariant image descriptors by setting up a min-max game where the discriminator tries to minimize the domain classification loss given three datasets (source, pseudo-target and a few samples from the target domain), while the feature extractor acts as an adversary to the discriminator.
+
+%----------------------------------------------------------------
+
 %-------------------------------------------------------------------------
@@
 At the end, we tried averaging the weights of models trained in the previous steps using Model Soups' approach~\cite{modelsoup} to improve recalls.
+
+\begin{figure*}
+  \centering
+  \begin{subfigure}{0.58\linewidth}
+    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
+    \caption{Example of images from San Francisco XS dataset.}
+    \label{fig:short-a}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.38\linewidth}
+    \fbox{\rule{0pt}{1.5in} \includegraphics[width=0.9\linewidth]{assets/no_images_per_class.jpeg}}
+    \caption{Numbers of images per class in San Francisco XS dataset.}
+    \label{fig:sfxs_density}
+  \end{subfigure}
+  \caption{Example of a short caption, which should be centered.}
+  \label{fig:short}
+\end{figure*}
+
+\subsection{Datasets}
+For our work, we have been provided with two datasets to experiment with: San Francisco eXtra Small (\textbf{SF-XS}) and Tokyo eXtra Small (\textbf{Tokyo-XS}).
+These datasets are respectively subsets of SF-XL~\cite{Berton_CVPR_2022_CosPlace} and Tokyo 24/7~\cite{tokyo247} purposely reduced for our convenience due to limitations in compute availability.
+SF-XS contains 59704 images for the train (both queries and database), 16008 for the evaluation (8015 as database, 7993 as queries) and 28191 for the test (27191 as database, 1000 as queries).
+Tokyo-XS only contains 13086 images for the test (12771 as database, 305 as queries).
+All these datasets are provided with labels that can be derived from the images' names as \textit{\{east, north, heading\}} and specifically for the training dataset, there are 5965 different classes, each one of them containing 10 images, as shown in \cref{fig:sfxs_density}.
+Finally, to understand if the changes applied to our model help in geolocalizing night images, we created a new dataset called \textbf{Tokyo-Night}: it is a subset of Tokyo-XS of which only the night images from queries are retained (1 out of 3, so 105 query images in total).
+
 \subsection{CosPlace}
@@
 This allows for the model to be used also on other datasets from unseen geographical areas, like Tokyo-XS and the smaller Tokyo-Night.
+
+\begin{figure*}
+  \centering
+  \begin{subfigure}{1.0\linewidth}
+    \centering
+    \fbox{ \includegraphics[width=\dimexpr\textwidth-2\fboxrule-2\fboxsep]{assets/architecture.png}}
+
+  \end{subfigure}
+     \caption{The proposed architecture.
+First, a domain-driven data augmentation method is used to generate a labeled pseudo-target dataset from the source dataset and just 5 unlabeled target images.
+Then, the source dataset, pseudo-target dataset, and the 5 unlabeled target images are used to train the network that extracts the image descriptors.
+This network leverages an aggregation module and a domain adaptation module to provide robustness to shifting.}
+    \label{fig:our_architecture}
+  \hfill
+\end{figure*}
+
 \subsection{Custom Augmentations}
-To assess the robustness of CosPlace~\cite{Berton_CVPR_2022_CosPlace} and improve its capability to learn a good embedding space even on sub-optimal picture quality we conducted a study on the augmentation pipeline already present in the original implementation (Color Jitter, RandomResizedCrop, Normalize) that we named \textbf{base} for our ablation, by adding 4 new augmentations on the images with a probability of 25\% and a fixed seed for reproducibility purposes.
+To assess the robustness of CosPlace~\cite{Berton_CVPR_2022_CosPlace}, its capability to learn a good embedding space even on sub-optimal picture quality and try to find augmentations to achieve better generalization,
+we conducted a study on the augmentation pipeline already present in the original implementation following SFRS \cite{sfrs} during the training step (Color Jitter, RandomResizedCrop, Normalize) that we named \textbf{base}, by adding 4 new augmentations on the images after Color Jittering, with a probability of 25\% of being applied and a fixed seed for reproducibility purposes.
 Those augmentations consisted of:
 \begin{itemize}
-  \item Gaussian Blur
-  \item Gray scale
-  \item Horizontal Flip
-  \item Erasing
+  \item \textbf{Gaussian Blur}\newline
+Blurring images can show the robustness of CosPlace on realistic use case in which the provided images are not always clear.
+  \item \textbf{Grayscale}\newline
+  In the context of place recognition Grayscale has already been successfully employed in \cite{grayscalecnn} to reduce the effect of illumination variation, which suits also our case.
+  \item \textbf{Horizontal Flip}\newline
+The datasets in use contain informations on orientation and heading of the images, applying an horizontal flip should prove consistency on the query images. 
+  \item \textbf{Erasing}\newline
+Randomly erasing an amount of pixels in the picture, can simulate the realistic case of occlusion and usually improves the CNN-based recognition models as \cite{reda}.
 \end{itemize}
-[TODO] Insert here description of the custom augmentations made, how they were implemented, citing where inspiration was taken.
+
+\begin{figure}[b]
+    \centering
+    \fbox{ 
+    \begin{tabular}{cc}
+  \includegraphics[width=35mm]{assets/source-example.jpg} &   \includegraphics[width=35mm]{assets/pseudo-example.jpg} \\
+  \end{tabular}
+  }
+    \caption{On the left the source image, on the right the pseudo-target image generated with FDA + saturation and temperature convertion.}
+    \label{fig:fda_show}
+\end{figure}
+
 \subsection{FDA and GRL}
-\textbf{FDA}
+\textbf{Domain-Drive Data Augmentation.}
 The purpose of the domain-driven data augmentation (DDDA) module is to find a mapping $D_s \mapsto D_{pt}$ from the source domain to a pseudo-target domain that better approximates the target domain, i.e., $D_{pt} \approx D_t$.
 This mapping can then be applied to the source dataset $X_s$ to generate a new labeled dataset with pseudo-target images $X_{pt}$, it is a data augmentation technique and is performed only once, offline.
-Inspired by~\cite{fda, adageo}, we propose a DDDA method based on Fourier Domain Adaptation (FDA) to generate a pseudo-target dataset $X_{pt}$ given two randomly sampled images $x^s$ and $x^t$ from source and target.
+Inspired by~\cite{fda, adageo}, we used a DDDA method based on Fourier Domain Adaptation (\textbf{FDA})~\cite{fda} to generate a pseudo-target dataset $X_{pt}$ given two randomly sampled images $x^s$ and $x^t$ from source and target.
 First, the low frequency part of the amplitude of $x^s$ is replaced by that of $x^t$, then the modified spectral representation of the source is mapped back to an image whose content is the same as $x^s$ but will resemble the appearance of a sample from the target distribution.
+Since the pseudo-target images generated didn't look as "night" as thought, for all the processed images, we reduced their saturation to 70\% and converted their temperature towards blue, to give them a colder appearance, as shown in~\cref{fig:fda_show}
+Afterward, we use both $X_s$ and $X_{pt}$ to train the descriptor extraction network, leading to a more robust model.
 \newline
-Afterward, we use both $X_s$ and $X_{pt}$ to train the descriptor extraction network, leading to a more robust model.
+\textbf{Domain Adaptation Module.}
 In order for the retrieval to work well across domains it is important that the embeddings produced by the descriptor extraction network are domain agnostic, i.e., they do not encode domain-specific information.
@@
 The discriminator is composed of two fully connected layers, and its goal is to classify the domain to which the embeddings belong.
-Just before the discriminator, there is a gradient reversal layer (Ganin and Lempitsky, 2015) that in the forward pass acts as an identity transform, while in the backward pass multiplies the gradient by -$\lambda$, where $\lambda > 0$.
+Just before the discriminator, there is a gradient reversal layer (\textbf{GRL})~\cite{grl} that in the forward pass acts as an identity transform, while in the backward pass multiplies the gradient by -$\lambda$, where $\lambda > 0$.
 The use of this layer effectively sets up a min-max game, where the discriminator tries to minimize the domain classification loss, that is a cross-entropy loss $L_{CE}$, while the feature extractor learns to produce domain-invariant embeddings, acting as an adversary to the discriminator.
 
-\textbf{GRL.} We define a deep feed-forward architecture that for each input $x$ predicts its class $y \in Y$ and its domain label $d \in \{0, 1\}$, depending if it is an image from day or night.
-[TODO] To finish...
+\textbf{Architecture details.}
+The idea is that for each input $x$, we predict its class $y \in Y$ and its domain label $d \in \{0, 1\}$, depending if it is an image from day or night.
+We assume that the input $x$ is the output of the frozen layers of our CNN backbone, which we call feature vector $f$.
+Then, we fine-tune the last layers of the CNN, the upper branch aggregator in \cref{fig:our_architecture} pools $f$ (if it comes from the labeled source) with GeM Pooling to finish the image descriptor extraction, and we denote the parameters of this section with $\theta_f$.
+Then the descriptor is mapped to its class label probabilities $y$ by CosFace, with parameters $\theta_y$.
+Finally, the same feature vector $f$ is mapped to the domain label $d$ by the lower branch in \cref{fig:our_architecture} (\textit{domain classifier}), with $\theta_d$ as parameters.
+During the learning stage, we aim to minimize the label
+prediction loss on the labeled part (i.e. the source part)
+of the training set, and the parameters of both the feature
+extractor $\theta_f$ and the label predictor $\theta_y$ are thus optimized in order to minimize the cross-entropy loss for the source domain samples $L_y$.
+At the same time, to make the features $f$ domain-invariant we seek $\theta_f$ that maximize the loss of the domain classifier $L_d$, while simultaneously seeking $\theta_d$ that minimizes the latter.
+The trade-off between the two objectives is controlled by a parameter $\lambda$.
+The parameters update are similar to the ones of stochastic gradient descent (SGD) for a feed-forward deep model that
+comprises feature extractor fed into the label predictor and
+into the domain classifier, but the difference here is given from $\lambda$ so a direct implementation of SGD is not possible.
+This can, instead, be accomplished by a Gradient Reversal Layer (GRL)  which during the forward propagation acts as an identity transform and during the backpropagation takes the gradient from
+the subsequent level, multiplies it by $-\lambda$ and passes it to
+the preceding layer.
+At the end of the training phase, the two losses ($L_y$, $L_d$) are combined as $L_y + \alpha \cdot L_d$ where $\alpha = 0.1$.
 
 \subsection{Model Soup}
+Training a learning model is usually done in two steps: first, the model is trained several times by varying the hyper parameters, and then the model with the best performance is chosen before being used.
+The publication ”Model soups: averaging weights of multiple fine-tuned models improves accuracy without increasing inference time”~\cite{modelsoup} proposes to average the weights of the different models to maximize the use of all the training without wasting learning time.
+This adds very little memory cost, learning time or inference time.
+The paper shows that a performance increase is visible on some models and even defines a new state of the art on image classification.
+The authors present two ways to combine two (or more) models to create a soup: greedy soup and uniform soup.
+In this project we tried to implement greedy version of the proposed solution and then we test the model on the datasets available.
 [TODO] Insert here description of how Model Soup has been implemented.
@@
 The couple of augmentation \textbf{blur, grayscale} seems the best choice for the augmentation pipeline, since not only the model manages to show robustness to that data augmentation pipeline, but also gets improvements.
-Further investigations should be performed with different parameters to deeply understand those results, however it seems that grayscale performs better since it show invariance to the colors of the scenes changing through the day.
-[TODO valutare se aggiungere ref.]
-[TODO guardare extension b]
+Further investigations should be performed with different parameters (\eg number of iterations, batch size, augmentation intensity, etc.) to deeply understand their behavior, however it seems that applying grayscale to the model leads to better performances, since it might add invariance to the colors of the scenes changing through the day.
 \newline
@@
     FDA+GRL & \textbf{53.7/66.5} & \textbf{70.5/84.8} & \textbf{53.3/73.3}\\
+    FDA+GRL+g & 53.4/65.5 & 67.6/84.8 & 48.6/72.4\\
     \bottomrule
   \end{tabular}
-  \caption{Baseline results compared with FDA only and FDA+GRL (with $\alpha=0.1$)}
+  \caption{Baseline results compared with FDA only, FDA+GRL (with $\alpha=0.1$) and FDA+GRL+grayscale.}
   \label{tab:fda+grl}
@@
 
-From these results, we surpass the baseline in all the three datasets by using both FDA and GRL together, reaching a \~4\% improvement on Tokyo-night.
-This confirms that the newly generated model was able to produce "more" domain-invariant features than before.
-Better can be expected, as the shift between this domain and the source domain (StreetView) is extreme, with very dark images and with a strong yellow tones.
+From these results, we surpass the baseline in all the three datasets by using both FDA and GRL together, reaching a $\sim4\%$ improvement on Tokyo-night.
+This confirms that the newly generated model was able to produce "more" domain-invariant features than before, with the downside of increasing the training time.
+Better can be expected by trying out different values for $\alpha$ or maybe performing a better post processing on the pseudo-target images generated.
+Finally, adding the best performing custom augmentation (grayscale with 25\% chance to be applied) didn't provide any improvement to the FDA+GRL model, showing that colors might play a discriminative role especially for the night domain.
+\newline
 
-\textbf{Qualitative Evaluation with Top K-NN}
+\textbf{Averaging model weights with Greedy soup algorithm.}
+To maximize model accuracy of our solution we pick all the best models trained and then merge them in a single model capable to improve performances without increasing inference time.
+The greedy soup is constructed by sequentially adding each model as a potential ingredient in the soup, and only keeping the model in the soup if performance on a held out validation set improves.
+For this purpose we decided to sort the models in a decreasing order of their recall values got in the training step, in this way the soup have to be certainly better or equal than the best model analyzed.
+Unfortunately, due to Colab limitations (in terms of batch size and epochs number for the training step) we didn't achieve any real improvement on our best model (FDA+GRL) after testing on all the datasets available.
 \newline
+
+\textbf{Qualitative Evaluation with Top K-NN.}
 To assess the goodness of the results obtained applying FDA and GRL in particular on Tokyo-Night dataset, we look at the nearest neighbors in the feature space, to understand the trained model's reasoning on different proposed queries.
@@
 In order to retrieve the top K = 5 most similar images to a given one, we calculate the Euclidean distance between the target image's embedding and each image's embedding in the dataset, one by one.
-For our experiment, we used and tested Tokyo-Night [TODO REF] as database for the queries retrieval in fig. \ref{fig:tokyonighttopknn} in two different ways.
-The model was trained with FDA and GRL active [TODO review..], however in the set A)\newline we didn't apply FDA to the images just to be sure that our trained model worked as intended with the original set both on day and night queries and the result was perfect for the first 3 neighbors.
-In the set B) we applied FDA to the dataset and used as query the same image treated with FDA (on the left) and another among its correct night queries (on the right).
+For our experiment, we used and tested Tokyo-Night as database for the queries retrieval in fig. \cref{fig:tokyonighttopknn} in two different ways.
+The model was trained with both FDA and GRL active, however:
+\begin{itemize}
+    \item in the set \textbf{A} we didn't apply FDA to the dataset used for the Top K-NN retrieval, just to be sure that our trained model worked as intended with the original set, both on day and night queries.
+The result was perfect for the first 3 neighbors.
+    \item in the set \textbf{B} we applied FDA to the dataset used for the Top K-NN retrieval and used as queries the same image treated with FDA (on the left) and from the night domain (on the right).
     Once again the result was satisfactory and the FDA-treated image was perfectly recognized and integrated in both cases, proving the correct reasoning of our proposed model.
+\end{itemize}
 
@@
     \fbox{ \includegraphics[width=\dimexpr\textwidth-2\fboxrule-2\fboxsep]{assets/topknn.png}}
-    \caption{2a TODO CAPTION, attention to ref}
+  \end{subfigure}
+      \caption{Given a target image, top 5 matching images are shown. Preset A) corresponds to Tokyo-Night dataset without FDA applied.
+Preset B) corresponds to Tokyo-Night dataset with FDA applied on the target image on the left.}
+  \hfill
   \label{fig:tokyonighttopknn}
-  \end{subfigure}
-  \hfill
 \end{figure*}
@@
 
-\section{Stuff to copy for Latex}
-
-\subsection{The ruler}
-The \LaTeX\ style defines a printed ruler which should be present in the version submitted for review.
-The ruler is provided in order that reviewers may comment on particular lines in the paper without circumlocution.
-If you are preparing a document using a non-\LaTeX\ document preparation system, please arrange for an equivalent ruler to appear on the final output pages.
-The presence or absence of the ruler should not change the appearance of any other content on the page.
-The camera-ready copy should not contain a ruler.
-(\LaTeX\ users may use options of cvpr.sty to switch between different versions.)
-
-Reviewers:
-note that the ruler measurements do not align well with lines in the paper --- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
-Just use fractional references (\eg, this line is $087.5$), although in most cases one would expect that the approximate location will be adequate.
-
-\subsection{Paper ID}
-Make sure that the Paper ID from the submission system is visible in the version submitted for review (replacing the ``*****'' you see in this document).
-If you are using the \LaTeX\ template, \textbf{make sure to update paper ID in the appropriate place in the tex file}.
-
-\subsection{Mathematics}
-
-Please number all of your sections and displayed equations as in these examples:
-\begin{equation}
-  E = m\cdot c^2
-  \label{eq:important}
-\end{equation}
-and
-\begin{equation}
-  v = a\cdot t.
-  \label{eq:also-important}
-\end{equation}
-It is important for readers to be able to refer to any particular equation.
-Just because you did not refer to it in the text does not mean some future reader might not need to refer to it.
-It is cumbersome to have to use circumlocutions like ``the equation second from the top of page 3 column 1''.
-(Note that the ruler will not be present in the final copy, so is not an alternative to equation numbers).
-All authors will benefit from reading Mermin's description of how to write mathematics:
-\url{http://www.pamitc.org/documents/mermin.pdf}.
-
-\subsection{Blind review}
-
-Many authors misunderstand the concept of anonymizing for blind review.
-Blind review does not mean that one must remove citations to one's own work---in fact it is often impossible to review a paper unless the previous citations are known and available.
-
-Blind review means that you do not use the words ``my'' or ``our'' when citing previous work.
-That is all.
-(But see below for tech reports.)
-
-Saying ``this builds on the work of Lucy Smith [1]'' does not say that you are Lucy Smith;
-it says that you are building on her work.
-If you are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith and Jones show in [7]'' and at the end of the paper, include reference 7 as you would any other cited work.
-
-An example of a bad paper just asking to be rejected:
-\begin{quote}
-\begin{center}
-    An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of our previous paper [1], and show it to be inferior to all previously known methods.
-   Why the previous paper was accepted without this analysis is beyond me.
-
-   [1] Removed for blind review
-\end{quote}
-
-An example of an acceptable paper:
-\begin{quote}
-\begin{center}
-     An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of the  paper of Smith \etal [1], and show it to be inferior to all previously known methods.
-   Why the previous paper was accepted without this analysis is beyond me.
-
-   [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a fundamental contribution to human knowledge''. Nature 381(12), 1-213.
-\end{quote}
-
-If you are making a submission to another conference at the same time, which covers similar or overlapping material, you may need to refer to that submission in order to explain the differences, just as you would if you had previously published related work.
-In such cases, include the anonymized parallel submission~\cite{Authors14} as supplemental material and cite it as
-\begin{quote}
-[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324, Supplied as supplemental material {\tt fg324.pdf}.
-\end{quote}
-
-Finally, you may feel you need to tell the reader that more details can be found elsewhere, and refer them to a technical report.
-For conference submissions, the paper must stand on its own, and not {\em require} the reviewer to go to a tech report for further details.
-Thus, you may say in the body of the paper ``further details may be found in~\cite{Authors14b}''.
-Then submit the tech report as supplemental material.
-Again, you may not assume the reviewers will read this material.
-
-Sometimes your paper is about a problem which you tested using a tool that is widely known to be restricted to a single institution.
-For example, let's say it's 1969, you have solved a key problem on the Apollo lander, and you believe that the CVPR70 audience would like to hear about your
-solution.
-The work is a development of your celebrated 1968 paper entitled ``Zero-g frobnication: How being the only people in the world with access to the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
-
-You can handle this paper like any other.
-Do not write ``We show how to improve our previous work [Anonymous, 1968].
-This time we tested the algorithm on a lunar lander [name of lander removed for blind review]''.
-That would be silly, and would immediately identify the authors.
-Instead write the following:
-\begin{quotation}
-\noindent
-   We describe a system for zero-g frobnication.
-   This system is new because it handles the following cases:
-   A, B.  Previous systems [Zeus et al. 1968] did not  handle case B properly.
-   Ours handles it by including a foo term in the bar integral.
-
-   ...
-
-   The proposed system was integrated with the Apollo lunar lander, and went all the way to the moon, don't you know.
-   It displayed the following behaviours, which show how well we solved cases A and B: ...
-\end{quotation}
-As you can see, the above text follows standard scientific convention, reads better than the first version, and does not explicitly name you as the authors.
-A reviewer might think it likely that the new paper was written by Zeus \etal, but cannot make any decision based on that guess.
-He or she would have to be sure that no other authors could have been contracted to solve problem B.
-\medskip
-
-\noindent
-FAQ\medskip\\
-{\bf Q:} Are acknowledgements OK?\\
-{\bf A:} No.  Leave them for the final copy.\medskip\\
-{\bf Q:} How do I cite my results reported in open challenges?
-{\bf A:} To conform with the double-blind review policy, you can report results of other challenge participants together with your results in your paper.
-For your results, however, you should not identify yourself and should not mention your participation in the challenge.
-Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\
-
-\begin{figure}[t]
-  \centering
-  \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-
-   \caption{Example of caption.
-   It is set in Roman so that mathematics (always set in Roman: $B \sin A = A \sin B$) may be included without an ugly clash.}
-   \label{fig:onecol}
-\end{figure}
-
-\subsection{Miscellaneous}
-
-\noindent
-Compare the following:\\
-\begin{tabular}{ll}
- \verb'$conf_a$' &  $conf_a$ \\
- \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-\end{tabular}\\
-See The \TeX book, p165.
-
-The space after \eg, meaning ``for example'', should not be a sentence-ending space.
-So \eg is correct, {\em e.g.} is not.
-The provided \verb'\eg' macro takes care of this.
-
-When citing a multi-author paper, you may save space by using ``et alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word).
-If you use the \verb'\etal' macro provided, then you need not worry about double periods when used at the end of a sentence as in Alpher \etal.
-However, use it only when there are three or more authors.
-Thus, the following is correct:
-   ``Frobnication has been trendy lately.
-   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
-
-This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...'' because reference~\cite{Alpher03} has just two authors.
-
-% Update the cvpr.cls to do the following automatically.
-% For this citation style, keep multiple citations in numerical (not
-% chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
-% \cite{Alpher02,Alpher03,Authors14}.
-
-\begin{figure*}
-  \centering
-  \begin{subfigure}{0.68\linewidth}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-    \caption{An example of a subfigure.}
-    \label{fig:short-a}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}{0.28\linewidth}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-    \caption{Another example of a subfigure.}
-    \label{fig:short-b}
-  \end{subfigure}
-  \caption{Example of a short caption, which should be centered.}
-  \label{fig:short}
-\end{figure*}
-
-%------------------------------------------------------------------------
-\section{Formatting your paper}
-\label{sec:formatting}
-
-All text must be in a two-column format.
-The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
-Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
-The main title (on the first page) should begin 1 inch (2.54 cm) from the top edge of the page.
-The second and following pages should begin 1 inch (2.54 cm) from the top edge.
-On all pages, the bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
-for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the
-page.
-
-%-------------------------------------------------------------------------
-\subsection{Margins and page numbering}
-
-All printed material, including text, illustrations, and charts, must be kept
-within a print area $6\frac{7}{8}$ inches (17.46 cm) wide by $8\frac{7}{8}$ inches (22.54 cm)
-high.
-%
-Page numbers should be in the footer, centered and $\frac{3}{4}$ inches from the bottom of the page.
-The review version should have page numbers, yet the final version submitted as camera ready should not show any page numbers.
-The \LaTeX\ template takes care of this when used properly.
-
-%-------------------------------------------------------------------------
-\subsection{Type style and fonts}
-
-Wherever Times is specified, Times Roman may also be used.
-If neither is available on your word processor, please use the font closest in
-appearance to Times to which you have access.
-
-MAIN TITLE.
-Center the title $1\frac{3}{8}$ inches (3.49 cm) from the top edge of the first page.
-The title should be in Times 14-point, boldface type.
-Capitalize the first letter of nouns, pronouns, verbs, adjectives, and adverbs;
-do not capitalize articles, coordinate conjunctions, or prepositions (unless the title begins with such a word).
-Leave two blank lines after the title.
-
-AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type.
-This information is to be followed by two blank lines.
-
-The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-MAIN TEXT.
-Type main text in 10-point Times, single-spaced.
-Do NOT use double-spacing.
-All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
-Make sure your text is fully justified---that is, flush left and flush right.
-Please do not place any additional blank lines between paragraphs.
-
-Figure and table captions should be 9-point Roman type as in \cref{fig:onecol,fig:short}.
-Short captions should be centred.
-
-\noindent Callouts should be 9-point Helvetica, non-boldface type.
-Initially capitalize only the first word of section titles and first-, second-, and third-order headings.
-
-FIRST-ORDER HEADINGS.
-(For example, {\large \bf 1. Introduction}) should be Times 12-point boldface, initially capitalized, flush left, with one blank line before, and one blank line after.
-
-SECOND-ORDER HEADINGS.
-(For example, { \bf 1.1. Database elements}) should be Times 11-point boldface, initially capitalized, flush left, with one blank line before, and one after.
-If you require a third-order heading (we discourage it), use 10-point Times, boldface, initially capitalized, flush left, preceded by one blank line, followed by a period and your text on the same line.
-
-%-------------------------------------------------------------------------
-\subsection{Footnotes}
-
-Please use footnotes\footnote{This is what a footnote looks like.
-It often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral observations in the text (within parentheses, if you prefer, as in this sentence).
-If you wish to use a footnote, place it at the bottom of the column on the page on which it is referenced.
-Use Times 8-point type, single-spaced.
-
-%-------------------------------------------------------------------------
-\subsection{Cross-references}
-
-For the benefit of author(s) and readers, please use the
-{\small\begin{verbatim}
-  \cref{...}
-\end{verbatim}}  command for cross-referencing to figures, tables, equations, or sections.
-This will automatically insert the appropriate label alongside the cross-reference as in this example:
-\begin{quotation}
-  To see how our method outperforms previous work, please see \cref{fig:onecol} and \cref{tab:example}.
-  It is also possible to refer to multiple targets as once, \eg~to \cref{fig:onecol,fig:short-a}.
-  You may also return to \cref{sec:formatting} or look at \cref{eq:also-important}.
-\end{quotation}
-If you do not wish to abbreviate the label, for example at the beginning of the sentence, you can use the
-{\small\begin{verbatim}
-  \Cref{...}
-\end{verbatim}}
-command. Here is an example:
-\begin{quotation}
-  \Cref{fig:onecol} is also quite important.
-\end{quotation}
-
-%-------------------------------------------------------------------------
-\subsection{References}
-
-List and number all bibliographical references in 9-point Times, single-spaced, at the end of your paper.
-When referenced in the text, enclose the citation number in square brackets, for
-example~\cite{Authors14}.
-Where appropriate, include page numbers and the name(s) of editors of referenced books.
-When you cite multiple papers at once, please make sure that you cite them in numerical order like this \cite{Alpher02,Alpher03,Alpher05,Authors14b,Authors14}.
-If you use the template as advised, this will be taken care of automatically.
-
-\begin{table}
-  \centering
-  \begin{tabular}{@{}lc@{}}
-    \toprule
-    Method & Frobnability \\
-    \midrule
-    Theirs & Frumpy \\
-    Yours & Frobbly \\
-    Ours & Makes one's heart Frob\\
-    \bottomrule
-  \end{tabular}
-  \caption{Results.   Ours is better.}
-  \label{tab:example}
-\end{table}
-
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-
-All graphics should be centered.
-In \LaTeX, avoid using the \texttt{center} environment for this purpose, as this adds potentially unwanted whitespace.
-Instead use
-{\small\begin{verbatim}
-  \centering
-\end{verbatim}}
-at the beginning of your figure.
-Please ensure that any point you wish to make is resolvable in a printed copy of the paper.
-Resize fonts in figures to match the font in the body text, and choose line widths that render effectively in print.
-Readers (and reviewers), even of an electronic copy, may choose to print your paper in order to read it.
-You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the figure width as a multiple of the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.pdf}
-\end{verbatim}
-}
-
-%-------------------------------------------------------------------------
-\subsection{Color}
-
-Please refer to the author guidelines on the \confName\ \confYear\ web page for a discussion of the use of color in your document.
-
-If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
-Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.
-
-%------------------------------------------------------------------------
-\section{Final copy}
-
-You must include your signed IEEE copyright release form when you submit your finished paper.
-We MUST have this form before your paper can be published in the proceedings.
-
-Please direct any questions to the production editor in charge of these proceedings at the IEEE Computer Society Press:
-\url{https://www.computer.org/about/contact}.
-
 %%%%%%%%% REFERENCES
 {\small
-\bibliographystyle{ieee_fullname}
+\clearpage
+\bibliographystyle{IEEEtran}
 \bibliography{egbib}

### 2023-02-05 paper/paper.tex
paper update

@@
 Their method casts the training as a classification problem and achieves state-of-the-art performances on a wide range of datasets and domain changes.
-We conducted a thorough ablation study of the loss function by comparing it with SphereFace and ArcFace loss functions and, finally, we carried out experiments on Domain Adaptation and Model Ensemble to try reach better benchmarks.
-[TODO REVIEW FINALE]
+We conducted a thorough ablation study of the loss function by comparing it with SphereFace~\cite{sphereface} and ArcFace~\cite{arcface} loss functions.
+Moreover, we carried out experiments on Domain Adaptation and Model Ensemble showing how a hybrid generative-discriminative approach helps robustness across domains, with special focus to the night one.
+Finally, we assessed the behavior of our best model in a qualitative way, showing the correct reasoning in the image retrieval task.
 Dataset, code and trained models are available for research purposes at: \newline
@@
 \newline
-\textbf{Training scalability}
+\textbf{Training scalability.}
 Having access to a massive amount of data raises the question of how to use it effectively for training. Many of the recent SOTA (state-of-the-art) methods take advantage
@@
 \newline
-\textbf{Contributions}
+\textbf{Contributions.}
 In this paper we want to investigate how the work of~\cite{Berton_CVPR_2022_CosPlace} can be improved for place recognition tasks, but using a smaller version of SF-XL dataset (called SF-XS) for the training, due to our limited resources.
-In particular we focus on trying to:
+In particular we focus on:
 \begin{itemize}
     \item generally improve the recalls on SF-XS and Tokyo-XS (a smaller version of Tokyo 24/7~\cite{tokyo247}), even with the help of ensembles to concatenate the descriptors of different models.
-    \item improve robustness to domain shift by borrowing techniques from the field of domain adaptation~\cite{adageo}, and testing the results on a dataset which only contains night images, called Tokyo-Night (a filtered version of Tokyo-XS).
+    \item improve robustness to domain shift by borrowing techniques from the field of domain adaptation~\cite{adageo}, and testing the results on a dataset which only contains night images, called Tokyo-Night (a filtered version of Tokyo-XS) and deeply understanding the applied domain adaptation techniques.
     \item assess how CosPlace behaves when data quality is scarce (\eg occlusion and blurry photos). 
@@
 
-[TODO conclusioni rapide]
+Through some experiments, we demonstrate that our solution exceeds the baseline provided by CosPlace on three different datasets and that the core ideas of the architecture (data augmentation, both domain-driven and non, and subsequent domain adaptation) provide modest increments to the performance.
 
@@
   \begin{subfigure}{0.58\linewidth}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-    \caption{Example of images from San Francisco XS dataset.}
+    \fbox{
+
+    \begin{tabular}{ccc}
+      \includegraphics[width=25mm]{assets/gridof6/example1.jpg} &   \includegraphics[width=25mm]{assets/gridof6/example2.jpg} &
+      \includegraphics[width=25mm]{assets/gridof6/example3.jpg}\\
+     \includegraphics[width=25mm]{assets/gridof6/example4.jpg} &   \includegraphics[width=25mm]{assets/gridof6/example5.jpg} &
+      \includegraphics[width=25mm]{assets/gridof6/example6.jpg}\\
+    \end{tabular}
+
+    }
+    \caption{Example of images from San Francisco XS dataset: they cover different time \\of the day, weather conditions, viewpoint and occlusions.}
     \label{fig:short-a}
@@
 Our work starts from CosPlace, an innovative approach in the field of visual geo-localization~\cite{Berton_CVPR_2022_CosPlace}.
-CosPlace casts the network training as an image classification problem: it partition the geographical area of interest in oriented cells, representing different classes, using UTM coordinates $\{east,north\}$\footnote{UTM coordinates are defined by a system used to identify locations on earth in meters, where 1 UTM unit corresponds to 1 meter.
+CosPlace casts the network training as an image classification problem: it partitions the geographical area of interest in oriented cells, representing different classes, using UTM coordinates $\{east,north\}$\footnote{UTM coordinates are defined by a system used to identify locations on earth in meters, where 1 UTM unit corresponds to 1 meter.
 They can be extracted from GPS coordinates (i.e., latitude and longitude) and allow approximating a restricted area of the earth’s surface on a flat surface.} and orientation/heading $\{heading\}$.
@@
 To assess the robustness of CosPlace~\cite{Berton_CVPR_2022_CosPlace}, its capability to learn a good embedding space even on sub-optimal picture quality and try to find augmentations to achieve better generalization,
-we conducted a study on the augmentation pipeline already present in the original implementation following SFRS \cite{sfrs} during the training step (Color Jitter, RandomResizedCrop, Normalize) that we named \textbf{base}, by adding 4 new augmentations on the images after Color Jittering, with a probability of 25\% of being applied and a fixed seed for reproducibility purposes.
+we conducted a study on the augmentation pipeline already present in the original implementation.
+Following SFRS \cite{sfrs} during the training step (Color Jitter, RandomResizedCrop, Normalize) that we named \textbf{base}, we added 4 new augmentations on the images after the default Color Jittering, with a 25\%  chance of being applied and a fixed seed for reproducibility purposes.
 Those augmentations consisted of:
@@
 \newline
+
 \textbf{Domain Adaptation Module.}
@@
 The use of this layer effectively sets up a min-max game, where the discriminator tries to minimize the domain classification loss, that is a cross-entropy loss $L_{CE}$, while the feature extractor learns to produce domain-invariant embeddings, acting as an adversary to the discriminator.
+\newline
 
@@
 Training a learning model is usually done in two steps: first, the model is trained several times by varying the hyper parameters, and then the model with the best performance is chosen before being used.
-The publication ”Model soups: averaging weights of multiple fine-tuned models improves accuracy without increasing inference time”~\cite{modelsoup} proposes to average the weights of the different models to maximize the use of all the training without wasting learning time.
+The publication ”Model soups: averaging weights of multiple fine-tuned models improves accuracy without increasing inference time”~\cite{modelsoup} proposes to average the weights of the different models to maximize the use of all the training [TODO training cosa??] without wasting learning time.
 This adds very little memory cost, learning time or inference time.
@@
 Better can be expected by trying out different values for $\alpha$ or maybe performing a better post processing on the pseudo-target images generated.
-Finally, adding the best performing custom augmentation (grayscale with 25\% chance to be applied) didn't provide any improvement to the FDA+GRL model, showing that colors might play a discriminative role especially for the night domain.
+Finally, adding the best performing custom augmentation (grayscale with 25\% chance to be applied) didn't provide any improvement to the FDA+GRL model, showing that if real colors are available, they will outperform the generalization improvement of grayscale.
 \newline
@@
 For this purpose we decided to sort the models in a decreasing order of their recall values got in the training step, in this way the soup have to be certainly better or equal than the best model analyzed.
-Unfortunately, due to Colab limitations (in terms of batch size and epochs number for the training step) we didn't achieve any real improvement on our best model (FDA+GRL) after testing on all the datasets available.
+Unfortunately, due to Colab limitations (in terms of batch size and epochs number for the training step) we had a limited number of models to use and we didn't achieve any real improvement on our best model (FDA+GRL) after testing on all the datasets available.
+This can happen if every time the next model in the list is added, it gets discarded because it doesn't provide any performance increment.
+This could be one of the approaches to be further explored, in the future, with more advanced tools.
 \newline
@@
 
-\begin{figure*}
+\begin{figure*}[t]
 \centering
@@
 \section{Conclusions}
-[TODO] Insert here conclusions and possible further implementations.
+In this paper, we proposed different improvements to CosPlace.
+In order to obtain better performances than the baseline on the night dataset, different from the training one for colors, brightness and city where the pictures were taken, we demonstrated that it is possible to improve domain shifting by applying FDA on the training dataset and using a Domain Adaptation module that forces the feature extractor to produce domain-invariant representations.
+We have also found that this solution improves the recalls of SF-XS and Tokyo-XS as well, and we assessed our results with a Top K-NN retrieval.
+\newline
+Furthermore, we confirmed our hypothesis of applying grayscale on images to improve illumination invariance.
+\newline
+Finally, we tried boosting recalls of our model with a Greedy Soup approach, but didn't get any enhancement or worsening.
+\newline
+
+We believe that this work can be still improved, possibly with the use of an attention layer before the aggregator, as done in~\cite{adageo} that, given this field and on top of our proposals, might show interesting results.
 

### 2023-02-06 eval.py
final version

@@ -1,44 +1,0 @@
-
-import sys
-import torch
-import logging
-import multiprocessing
-from datetime import datetime
-
-import test
-import our_parser
-import commons
-from model import network
-from datasets.test_dataset import TestDataset
-
-torch.backends.cudnn.benchmark = True  # Provides a speedup
-
-args = our_parser.parse_arguments(is_training=False)
-start_time = datetime.now()
-output_folder = f"logs/{args.save_dir}/{start_time.strftime('%Y-%m-%d_%H-%M-%S')}"
-commons.make_deterministic(args.seed)
-commons.setup_logging(output_folder, console="info")
-logging.info(" ".join(sys.argv))
-logging.info(f"Arguments: {args}")
-logging.info(f"The outputs are being saved in {output_folder}")
-
-#### Model
-model = network.GeoLocalizationNet(args.backbone, args.fc_output_dim)
-
-logging.info(f"There are {torch.cuda.device_count()} GPUs and {multiprocessing.cpu_count()} CPUs.")
-
-if args.resume_model is not None:
-    logging.info(f"Loading model from {args.resume_model}")
-    model_state_dict = torch.load(args.resume_model)
-    model.load_state_dict(model_state_dict)
-else:
-    logging.info("WARNING: You didn't provide a path to resume the model (--resume_model parameter). " +
-                 "Evaluation will be computed using randomly initialized weights.")
-
-model = model.to(args.device)
-
-test_ds = TestDataset(args.test_set_folder, queries_folder="queries_v1",
-                      positive_dist_threshold=args.positive_dist_threshold)
-
-recalls, recalls_str = test.test(args, test_ds, model)
-logging.info(f"{test_ds}: {recalls_str}")

### 2023-02-06 notes.py

@@ -1,21 +1,0 @@
-import sys
-import our_parser
-import logging
-import commons
-import plots
-from datetime import datetime
-from datasets.test_dataset import TestDataset
-from datasets.train_dataset import TrainDataset
-
-
-start_time = datetime.now()
-commons.make_deterministic()
-logging.info(" ".join(sys.argv))
-args = our_parser.parse_arguments()
-
-
-#### Datasets
-groups = [TrainDataset(args, args.train_set_folder) for n in range(args.groups_num)]
-
-for g in groups:
-    plots.plot_histogram(g.classes_ids, g.images_per_class)

### 2023-02-06 test_only.py

@@ -34,7 +34,7 @@ logging.info(f"The outputs are being saved in {output_folder}")
 model = network.GeoLocalizationNet(args.backbone, args.fc_output_dim)
 
 
-model = model.to(args.device).train()
+model = model.to(args.device)
 
 
 test_ds = TestDataset(args.test_set_folder, queries_folder="queries_v1",

### 2023-02-06 train.py

@@ -1,3 +1,4 @@
+
 import sys
 import torch
 import logging
@@ -6,33 +7,35 @@ from tqdm import tqdm
 import multiprocessing
 from datetime import datetime
 import torchvision.transforms as T
-
+import custom_augmentations as CA
 import test
 import util
 import our_parser
 import commons
 import cosface_loss
 import new_cosface_loss
-import arcface_loss
 import sphereface_loss
+import arcface_loss
 import augmentations
 from model import network
 from datasets.test_dataset import TestDataset
 from datasets.train_dataset import TrainDataset
+from datasets.grl_datasets import GrlDataset
+import random 
 
 torch.backends.cudnn.benchmark = True  # Provides a speedup
 
 args = our_parser.parse_arguments()
 start_time = datetime.now()
-output_folder = f"logs/{args.save_dir}/{start_time.strftime('%Y-%m-%d_%H-%M-%S')}"
+output_folder = f"AML23-CosPlace/model/results/best_{start_time.strftime('%Y-%m-%d_%H-%M-%S')}"
 commons.make_deterministic(args.seed)
 commons.setup_logging(output_folder, console="debug")
 logging.info(" ".join(sys.argv))
 logging.info(f"Arguments: {args}")
 logging.info(f"The outputs are being saved in {output_folder}")
 
-#### Model
-model = network.GeoLocalizationNet(args.backbone, args.fc_output_dim)
+#### Model (+ GRL for domain adaptation)
+model = network.GeoLocalizationNet(args.backbone, args.fc_output_dim, grl = args.grl)
 
 logging.info(f"There are {torch.cuda.device_count()} GPUs and {multiprocessing.cpu_count()} CPUs.")
 
@@ -45,11 +48,16 @@ model = model.to(args.device).train()
 
 #### Optimizer
 criterion = torch.nn.CrossEntropyLoss()
+epoch_grl_loss = 0 
+domain_adapt_criterion = torch.nn.CrossEntropyLoss() if args.grl == True else None #Loss for Domain Adaptation
 model_optimizer = torch.optim.Adam(model.parameters(), lr=args.lr)
 
 #### Datasets
 groups = [TrainDataset(args, args.train_set_folder, M=args.M, alpha=args.alpha, N=args.N, L=args.L,
                        current_group=n, min_images_per_class=args.min_images_per_class) for n in range(args.groups_num)]
[…]

### 2023-02-06 plots.py
small fix

@@ -1,5 +1,14 @@
 import matplotlib.pyplot as plt
 
+
+def get_count(classes, images):
+    #return list containing [class_index]*no.instances per class
+    #[0,0,0,0...,1,1,1,...,2,2,2,2....]
+    count = []
+    for i in range(int(len(classes))):
+      count.extend([i]*len(images[classes[i]]))
+    return count
+
 #Histogram showing how many cells contain a given number of images. (Density?)
 
 
@@ -10,15 +19,15 @@ import matplotlib.pyplot as plt
 def plot_histogram(classes, images):
     #x = classes
     #y = num. of images
+
+    count = get_count(classes,images)
         
     plt.figure()
-    plt.title("Distribution")
+    plt.title("Number of images per class")
     plt.xlabel("Classes")
+    plt.ylabel("Count")
     
-    for i in range(len(classes)):
-        plt.hist(images[classes[i]], bins = 10, density = True, alpha = 0.4)
-
-    plt.legend()
-    #plt.savefig('%s/%s_%d.pdf' % (folder,name,index))
+    plt.hist(count, bins=range(int(len(classes))+1), alpha=1)
+    plt.savefig('%s/%s.jpeg' % ('/content','no_images_per_class'))
     plt.show()
 
